\newrecipe
\begin{recipe}
[
preparationtime = {\unit[40]{m}},
bakingtime = {\unit[20]{m}},
portion = {\portion{4-6}},
]
{Chicken Enchiladas}

\ingredients{
2 tablespoons butter\\ 
2 onions, thinly sliced\\ 
2 cups chopped cooked chicken\\ 
$\frac{1}{2}$ cup red pepper\\ 
8 ounces of cream cheese, cubed\\ 
$\frac{1}{4}$ teaspoon salt\\ 
$\frac{1}{4}$ teaspoon pepper\\ 
4 (4.5 ounce) cans diced green chiles\\ 
1 small onion, chopped\\ 
2 garlic cloves, minced\\ 
2 teaspoons dried oregano\\ 
1 teaspoon ground cumin\\ 
$\frac{1}{2}$ teaspoon sugar\\ 
1 (14-1/2 ounce) can chicken broth\\ 
$\frac{1}{2}$ cup green verde salsa\\ 
10 (7 inch) flour tortillas\\ 
2 cups (8 ounces) shredded Mexican cheese\\ 
}

\preparation{
\step Melt butter in a large skillet over medium high heat, stirring often.
\step Add sliced onions and cook 20 minutes or until caramelized.
\step Reduce heat to low and add chopped chicken and next 4 ingredients, stirring until combined. Set aside.
\step Pulse chiles and next 5 ingredients in blender or food processor several times until combined.
\step Bring chile mixture and chicken broth to a boil in a saucepan over high heat; cook 5 minutes or until slightly thickened. (Mixture should be the consistency of a thin gravy.)
\step Remove from heat and stir in salsa.\\ 
\step Spread one third chile mixture evenly on bottom of a lightly greased 13 x 9 inch baking dish.
\step Spoon chicken mixture evenly down center of each tortilla; roll up and place seam side down in prepared baking dish.
\step Top with remaining chile mixture; sprinkle with cheese.\\ 
\step Bake at 375 degrees for 20 to 25 minutes or until bubbly.
}
\end{recipe}
