\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1.25]{h}},
portion = {\portion{4-6}},
source = Giada De Laurentis edited by Mom
]
{Roman style Chicken}

\ingredients{
3 skinless chicken breast halves, with ribs\\ 
4 skinless chicken thighs with bones\\ 
$1\frac{1}{2}$ teaspoon salt\\ 
$1\frac{1}{2}$ teaspoon freshly ground black pepper\\ 
$\frac{1}{4}$ cup olive oil\\ 
1 red bell pepper, sliced\\ 
1 yellow bell pepper, sliced\\ 
3 ounces prosciutto, chopped\\ 
2 cloves garlic, chopped\\ 
1 15 ounce can diced tomatoes\\ 
$\frac{1}{2}$ cup white wine\\ 
1 tablespoon fresh thyme leaves\\ 
1 teaspoon fresh oregano leaves\\ 
$\frac{1}{2}$ cup chicken broth\\ 
$\frac{1}{4}$ cup chopped fresh parsley leaves\\ 
Fresh Parmesan cheese\\ 
1 box fettuccine\\ 
}

\preparation{
\step Season the chicken with $\frac{1}{2}$ teaspoon salt and $\frac{1}{2}$ teaspoon pepper. \step In a heavy large skillet, heat the olive oil over medium heat.
\step When the oil is hot, cook the chicken until browned on both sides.
\step Remove chicken from the pan and set aside -- cover with foil or large boil to keep hot.
\step Keeping the same pan over medium heat, add the peppers and prosciutto and cook until the peppers have browned and the prosciutto is crisp, about 5 minutes.
\step Add the garlic and cook for 1 minute.\\ 
\step Add the tomatoes, wine and herbs. Then, using a wooden spoon, scrape the browned bits off the bottom of the pan. 
\step Return the chicken to the pan, add the stock and bring the mixture to a boil.
\step Reduce the heat and simmer covered, until the chicken is cooked through, about 20 to 30 minutes.
\step Meanwhile, cook the fettuccine and drain.\\ 
\step Add the fettuccine to a large pasta bowl. Add chicken over the top.\\ 
\step Sprinkle with fresh Parmesan cheese and chopped parsley leaves.
}
\end{recipe}
