\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
portion = {\portion{4-6}},
source = Paula Dean
]
{Baked French Toast Casserole with Maple Syrup}

\ingredients{
1 loaf French bread (13-16 ounces)\\ 
8 large eggs\\ 
2 cups half and half\\ 
1 cup milk\\ 
2 tablespoons granulated sugar\\ 
1 teaspoon vanilla extract\\ 
$\frac{1}{4}$ teaspoon ground cinnamon\\ 
$\frac{1}{4}$ teaspoon ground nutmeg\\ 
Dash salt\\ 
Maple Syrup\\ 
\\ 
\textbf{Praline Topping}:\hspace*{\fill} \\ 
2 sticks butter\\ 
1 cup packed brown sugar\\ 
1 cup chopped pecans\\ 
2 tablespoons light corn syrup\\ 
$\frac{1}{2}$ teaspoon ground cinnamon\\ 
$\frac{1}{2}$ teaspoon ground nutmeg\\ 
}

\preparation{
\step Slice French bread into 20 slices, 1 inch each. Arrange slices in a generously buttered 9 by 13 inch flat baking dish in 2 rows, overlapping the slices. 
\step In a large bowl, combine the eggs, half and half, milk, sugar, vanilla, cinnamon, nutmeg and salt and beat with a rotary beater or whisk until blended but not too bubbly. 
\step Pour mixture over the bread slices, making sure all are covered evenly with the milk-egg mixture. Spoon some of the mixture between the slices.
\step If prepping, Cover with foil and refrigerate whenever you are ready (overnight works well).
\step When ready to make, preheat the oven to 350 degrees.
\step For the praline topping, combine all the ingredients in a medium bowl and blend well.
\step Spread the praline topping evenly over the bread and bake for 40 minutes until puffed and lightly golden.
\step Serve with maple syrup.
}
\end{recipe}