\documentclass[a4paper,portrait,12pt]{book}
\usepackage[latin1]{inputenc}
\usepackage{calc}
\usepackage{setspace}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[normalem]{ulem}
%% Please revise the following command, if your babel
%% package does not support en-US
\usepackage[en]{babel}
\usepackage{color}
\usepackage{hyperref}

\title{Recipes}
\author{me }
\date{December 2018}
 
\begin{document}

\tableofcontents


Cookbook
Created December 2010



\newpage
Sweet and Sour Sausage






(Aunt Zina's recipe)




Ingredients:




2 pounds polish sausage




2 cups brown sugar




$\frac{1}{4}$ cup vinegar




$\frac{1}{4}$ cup sweet pickle juice




Directions:




Cut sausage in chunks. Boil $\frac{1}{2}$ hour.




Place boiled sausage in shallow baking dish. Add other ingredients.




Bake at 350 degrees for 1 hour or put all ingredients in crockpot and cook for approximately 3




hours on low.







\newpage
Stromboli




(Mom)




Ingredients:




Pizza dough (refrigerator, fresh or frozen-defrosted)




14 ounce can Tomato sauce (seasoned with Italian herbs) or fresh sauce




Italian sausage




Onions




1 Tablespoon butter




Pepperoni




Black olives




2 cups shredded Mozzerella cheese




Directions:




Brown Italian sausage. Melt butter in separate pan and added sliced onions and cook until soft.




Roll dough into a rectangle. Add Italian sausage, pepperoni, onions and black olives. Sprinkle




mozzarella cheese evenly over top. Roll up the dough lengthwise into a jelly roll. Pince seal and




lay on rectangle plan seal side down. Pince ends and tuck under.




Cook 375 degrees for 20-25 minutes depending on dough type.




Heat sauce and serve with stomboli.






\newpage
Harris Teeter's Rancher Chuck Roast




Ingredients:




3 pounds chuck roast




4 cloves garlic, minced




1 teaspoon kosher salt




2 teaspoons parsley




1 teaspoon ground black pepper




2 tablespoons shallots, minced




$\frac{1}{2}$ teaspoon basil, chopped




$\frac{1}{2}$ teaspoon thyme, chopped




$\frac{1}{2}$ pound bacon, diced




$\frac{1}{2}$ teaspoon oregano, chopped




1 cup red wine




Directions:




Preheat oven to 350 degrees. Place foil in baking dish. Place roast in foil, add salkt, pepper, garlic,




parsley, and shallots, Italian herbs on top of the road. Lay the diced bacon strips over the herbs and




seasonings. Add 1 cup red wine and wrap foil around tightly. Roast for 1-1 $\frac{1}{2}$ hours.







\newpage
Hawaiian Beef




(Great Grandma McCollum)




Ingredients:




2-4 pounds stew meat or cubed chuck steak




1 $\frac{1}{2}$ tablespoon brown sugar




$\frac{1}{2}$ teaspoon ginger




1 teaspoon dry mustard




1/8 teaspoon pepper




1 cup tomato sauce




2 tablespoons lemon juice




½-1 cup water




1 bay leaf




1 chopped onion




1 can crushed pineapple




Directions:




Brown Meat. Combine the rest of the ingredients into a sauce. Bake the meat and sauce covered




350 degrees 2 hours or in the crockpot on low for several hours.







\newpage
Holiday Rib Roast




(Harris Teeter recipe)




Ingredients:




5 rib bone-in rib roast (6 to 8 pounds)




1 tablespoon Worcestershire sauce




10 to 12 pounds of rock salt




1 cup water




Salt and pepper




1 large deep disposable aluminum plan




Directions:




Rub rib roast with worcestershire sauce.




Sprinkle salt and pepper over roast, be sure to cover entire piece of meat




Fill aluminum pan with 2 to 3 inches of rock salt




Place roast in plan bone side down into the rock salt




Pour remaining rock salt completely over roast, be sure to cover the entire piece of meat




Pour cup of water over salt




Place in pre-heated 500 degree oven for 1 hour




Turn oven down to 350 degrees and cook 20 minutes to the pound until done




Remove from oven at the end of cooking cycle and let sit for 5 minutes. To remove roast from




rock salt if will be necessary to break sale with a kitchen hammer.







\newpage
Braciole




(Giada De Laurentiis)




Ingredients:




$\frac{1}{2}$ cup dried Italian style bread crumbs




1 garlic clove, minced




2/3 cup grated Pecorino Romano




1/3 cup grated provolone




2 tablespoons chopped fresh Italian parsley leaves




4 tablespoons olive oil




Salt and freshly ground pepper




1 (1 $\frac{1}{2}$ pound) flank steak




1 cup dry white wine




3 $\frac{1}{4}$ cups marinara sauce




Directions:




Sire the first 5 ingredients in a medium bowl to blend. Stir in 2 tablespoons of the oil. Season




mixture with salt and pepper and set aside.




Lay the flank steak flat on the work surface. Sprinkle the bread crumb mixture evenly over the




steak to cover the top evenly. Starting at 1 short end, roll up the steak as a jelly roll to enclose the




filling completely. Using butcher's twine, tie the steak roll to secure. Sprinkle the braciole with




salt and pepper.




Preheat the oven to 350 degrees.




Heat the remaining 2 tablespoons of oil in a heavy large ovenproof skillet over medium heat. Add




the braciole and cook until browned on all sides, about 8 minutes. Add the wine to the pan and




bring to a boil. Sire in the marinara sauce. Cover partially with foil and bake until the meat is




almost tender, turning the braciole and basting with the sauce every 30 minutes. After 1 hour,




uncover and continue baking until the meat is tender, about 30 minutes longer. The total cooking




time should be about 1 $\frac{1}{2}$ hours.




Remove the braciole from the sauce. Using a large sharp knife, cut the braciole crosswise and




diagonally into $\frac{1}{2}$ inch thick slices. Transfer the slices to plates. Spoon the sauce over and serve.







\newpage
Beef and Guinness Stew




Ingredients:




2 pounds stewing beef




3 tablespoons oil




2 tablespoons flour




Salt and freshly ground black pepper




Pinch of cayenne




2 large onions, coarsely chopped




1 garlic clove, crushed




2 tablespoons tomato puree, dissolved in 4 tablespoons water




1 $\frac{1}{4}$ cups Guinness




2 cups largely diced carrots




Sprig of fresh thyme




Chopped parsley, for garnish




Directions:




Trim the meat of any fat or gristle and cut into 2 inch cubes. Toss beef with 1 tablespoon of the




oil. In a small bowl, season the flour with salt, pepper and cayenne. Toss meat with seasoned




flour. Heat remaining 2 tablespoons oil in a large skillet over high heat. Brown the meat on all




sides. Reduce the heat, add the onions, crushed garlic and tomato puree to the skillet, cover and




cook gently for 5 minutes. Transfer the contents of the skillet to a casserole and pour half of the




Guinness into the skillet. Bring Guinness to a boil and stir to dissolve the caramelized meat juices




on the pan. Pour over the meat, along with the remaining Guinness. Add the carrots and thyme.




Stir and adjust seasonings. Cover the casserole and simmer over low heat or in a 300 degree oven




until the meat is tender 2 to 3 hours. Garnish the beef with parsley.







\newpage
Foccacia with Savory and Olives




Ingredients:




1 $\frac{1}{2}$ cups warm water




1 tablespoon sugar




2 (1/4 ounce) packages active dry yeast




3 $\frac{1}{2}$ cups all purpose flour




2 teaspoons kosher salt




6 tablespoons extra-virgin olive oil, divided




1/3 cup black olives, sliced




$\frac{1}{4}$ cup slivered or sliced almonds




2 tablespoons chopped fresh savory




Coarse sea salt and freshly ground pepper




Directions:




In a small bowl, dissolve the sugar in the warm water. Sprinkle the yeast over the water and let




stand for 10 minutes. In the bowl of a mixer fitted with a paddle attachment, add 3 cups of the




flour, the salt, 2 tablespoons of the olive oil and the yeast mixture. Turn the mixer on low speed




and slowly mix until the dough comes together. Gradually add remaining flour. If the dough




seems too wet, add up to $\frac{1}{4}$ cup more flour. Place the dough into an oiled bowl, cover and let rise




in a warm place, free from drafts for 3 hours.




Preheat the oven to 375 degrees.




Punch down the dough and transfer onto a lightly greased 9 by 13 inch baking sheet. Spread the




dough to the edges of the baking sheet. Using your fingertips make dimples in the dough. Drizzle




the dough with the 2 tablespoons of the olive oil and sprinkle with the olives, almonds and savory.




Sprinkle lightly with salt and pepper. Bake for 30 to 35 minutes or until golden brown. Drizzle




with remaining 2 tablespoons of olive oil.







\newpage
Coffee Cake




Ingredients:




1 box yellow cake mix




1 package instant butterscotch pudding




4 eggs




$\frac{1}{2}$ cup oil




1 cup sour cream




Directions:




Grease a tube pan. Preheat oven 350 degrees.




Mix ingredients for 7 minutes.




Stir $\frac{1}{2}$ cup sugar, 2 teaspoons cinnamon and 1/3 cup nuts. Sprinkle sugar mixture on bottom of




pan. Spoon batter alternating the sugar mixture.




Bake 55-60 minutes. Cool upright in pan.







\newpage
Swedish Tea Ring




Ingredients:




2 cups milk




1 package yeast




$\frac{1}{4}$ cup water




2 tablespoons butter




2 tablespoons sugar




6 cups sifted flour




1 tablespoon melted butter




3 tablespoons butter




3 tablespoons brown sugar




1 tablespoon sugar




$\frac{1}{4}$ tsp cinnamon




Dash nutmeg




1/3 cup raisons




Directions:




Dough -- Scald milk (190 degrees). Soften yeast in lukewarm water (115 degrees). Measure butter,




sugar, and salt in mixing bowl. Add milk, stir until butter is melted. When milk is lukewarm, add




yeast. Add half of flour to mixture. Add more flour $\frac{1}{2}$ cup at a time. Turn dough on floured board




and allow to rest 10 minutes. Knead the dough until smooth and satiny. Shape dough and place in




oiled bowl. Cover with towel -- let rise out of draft (75 to 85 degrees) 1-1 $\frac{1}{2}$ to 2 hours.




Punch down dough -- divide in half




Roll $\frac{1}{2}$ of dough into an oblong 9x8x1/4 inch thick. Spoon dough with inside ingredients (sugars,




cinnamon, nutmeg and raisons.




Roll dough lengthwise, jelly roll fashion. Seal edge firmly. Shape into ring and seal ends together




by pinching dough. Cut through ring with scissors to $\frac{1}{2}$ inch from middle in slices 1 inch wide.




Twist each slice slightly on its side. Brush with melted butter and cover. Let rise till doubles in




size.




Bake at 375 degrees 25 minutes. Frost while warm with confectionery icing.







\newpage
Grandma's Doughnut Drops




Ingredients:




2 cups flour




1/3 cup sugar




3 teaspoons baking powder




1 teaspoon salt




1 teaspoon nutmeg




1 egg lightly beaten




¾ cup milk




3 tablespoons oil




Oil for fryer




Directions:




Sift dry ingredients together




Add egg, milk, oil and stir until smooth




Drop dough by teaspoonful into hot oil




Shake in cinnamon and sugar warm.







\newpage
Baked French Toast Casserole with Maple Syrup




(Paula Dean)




Ingredients:




1 loaf French bread (13 to 16 ounces)




8 large eggs




2 cups half and half




1 cup milk




2 tablespoons granulated sugar




1 teaspoon vanilla extract




$\frac{1}{4}$ teaspoon ground cinnamon




$\frac{1}{4}$ teaspoon ground nutmeg




Dash salt




Maple Syrup




Praline Topping:




2 sticks butter




1 cup packed brown sugar




1 cup chopped pecans




2 tablespoons light corn syrup




$\frac{1}{2}$ teaspoon ground cinnamon




$\frac{1}{2}$ teaspoon ground nutmeg




Directions:




Slice French bread into 20 slices, 1 inch each. Arrange slices in a generously buttered 9 by 13 inch




flat baking dish in 2 rows, overlapping the slices. In a large bowl, combine the eggs, half and half,




milk, sugar, vanilla, cinnamon, nutmeg and salt and beat with a rotary beater or whisk until




blended but not too bubbly. Pour mixture over the bread slices, making sure all are covered evenly




with the milk-egg mixture. Spoon some of the mixture between the slices. Cover with foil and




refrigerate overnight.




The next day, preheat the oven to 350 degrees.




For the praline topping, combine all the ingredients in a medium bowl and blend well.




Spread the praline topping evenly over the bread and bake for 40 minutes until puffed and lighly




golden. Serve with maple syrup.







\newpage
Pear Spice Muffins




Ingredients:




2 cups all-purpose flour




1 cup quick rolling oats




1 cup firmly packed light brown sugar




1 tablespoon baking powder




$\frac{1}{2}$ teaspoon salt




$\frac{1}{2}$ cup (1 stick) unsalted butter




1 teaspoon ground cinnamon




$\frac{1}{2}$ teaspoon ground allspice




2 eggs, lightly beaten




1 cup milk




1 cup grated, peeled pear (about 2 medium pears)




Directions:




Preheat oven to 375 degrees. Grease the cups of a 12 muffin pan or line with baking cups.




Combine the flour, oats, brown sugar, baking powder and salt in a mixing bowl. Using a pastry




blender or your fingers, cut in the butter until the mixture resembles coarse crumbs. Set aside ¾




cup for the topping; stir in the cinnamon and allspice into the reserved topping.




Stir together the eggs, milk and grated pear in a small bowl. Add the dry ingredients all at once,




stirring until just moist. Divide the batter evenly among 12 muffin cups, filling each cup two thirds




full. Sprinkle the topping evenly over the batter; pat down gently to make it stick. Bake for 25 to




30 minutes or until the tops spring back from lightly touched. Remove the muffins from the pan




immediately and cool on a wire rack.







\newpage
Pollo Salsa Verde




Ingredients:




4 boneless chicken breasts (thin sliced)




2 medium limes




2-2/3 cup verde salsa




15 8 inch flour tortillas




¾ cup sour cream




1 cup grated Monterey jack cheese




Directions:




Place chicken in 9 inch by 12 inch glass baking dish. Squeeze limes over chicken and season to




taste with fresh ground pepper and herbs. Marinate for 2 hours.




Preheat oven to 350 degrees. Bake uncovered for 20 minutes.




Remove from oven and cover chicken with 2/3 cup salsa. Cut tortillas into 1 inch strips. Cover the




top of the chicken with the strips into a checkerboard pattern, using only half the strips.




Spread another 2/3 cup salsa and add another layer of tortillas in the same checkerboard pattern.




Cover the tortillas with ¾ cup sour cream and back covered for 20 minutes.




After 20 minutes, remove from the oven, add one cup of grated Monterey jack cheese evenly over




the top.




Return to the oven and broil until the cheese turns golden brown (about 15 minutes)




Let stand 10 minutes before serving.







\newpage
Roman style Chicken




(Giada De Laurentis edited by Mom)




Ingredients:




3 skinless chicken breast halves, with ribs




4 skinless chicken thighs with bones




$\frac{1}{2}$ teaspoon salt, plus 1 teaspoon




$\frac{1}{2}$ teaspoon freshly ground black pepper, plus 1 teaspoon




$\frac{1}{4}$ cup olive oil




1 red bell pepper, sliced




1 yellow bell pepper, sliced




3 ounces prosciutto, chopped




2 cloves garlic, chopped




1 15 ounce diced tomatoes




$\frac{1}{2}$ cup white wine




1 tablespoon fresh thyme leaves




1 teaspoon fresh oregano leaves




$\frac{1}{2}$ cup chicken broth




$\frac{1}{4}$ cup chopped fresh flat leaf parsley leaves




Fresh parmesan cheese




Fettuccine




Directions:




Season the chicken with $\frac{1}{2}$ teaspoon salt and $\frac{1}{2}$ teaspoon pepper. In a heavy large skillet, heat the




olive oil over medium heat. When the oil is hot, cook the chicken until browned on both sides.




Remove from the pan and set aside -- cover with foil or large boil to keep hot.




Keeping the same pan over medium heat, add the peppers and prosciutto and cook until the




peppers have browned and the prosciutto is crisp, about 5 minutes. Add the garlic and cook for 1




minute. Add the tomatoes, wine and herbs. Using a wooden spoon, scrape the browned bits off the




bottom of the pan. Return the chicken to the pan, add the stock and bring the mixture to a boil.




Reduce the heat and simmer covered, until the chicken is cooked through, about 20 to 30 minutes.




Meanwhile, cook the fettuccine and drain.




Add the fettuccine to a large pasta bowl. Add chicken over the top. Sprinkle with fresh parmesan




and chopped parsley leaves.







\newpage
Chicken Enchiladas




Ingredients:




2 tablespoons butter




2 onions, thinly sliced




2 cups chopped cooked chicken




$\frac{1}{2}$ cup red pepper




8 ounces of cream cheese, cubed




$\frac{1}{4}$ teaspoon salt




$\frac{1}{4}$ teaspoon pepper




4 (4.5 ounce) cans diced green chiles




1 small onion, chopped




2 garlic cloves, minced




2 teaspoons dried oregano




1 teaspoon ground cumin




$\frac{1}{2}$ teaspoon sugar




1 (14-1/2 ounce) can chicken broth




$\frac{1}{2}$ cup green verde salsa




10 (7 inch) flour tortillas




2 cups (8 ounces) shredded Mexican or Cheddar cheese




Directions:




Melt butter in a large skillet over medium high heat, stirring often; add sliced onions and cook 20




minutes or until caramelized. Reduce heat to low and add chopped chicken and next 4 ingredients,




stirring until combined. Set aside.




Pulse chiles and next 5 ingredients in blender or food processer several times until combined.




Bring chile mixture and chicken broth to a boil in a saucepan over high heat; cook 5 minutes or




until slightly thickened. (Mixture should be the consistency of a thin gravy.) Remove from heat




and stir in salsa.




Spread one third chile mixture evenly on bottom of a lightly greased 13 x 9 inch baking dish.




Spoon chicken mixture evenly down center of each tortilla; roll up and place seam side down in




prepared baking dish. Top with remaining chile mixture; sprinkle with cheese.




Bake at 375 degrees for 20 to 25 minutes or until bubbly.







\newpage
Jambalaya




Ingredients:




12 medium shrimp, peeled, deveined and chopped




4 ounces chicken, diced




1 tablespoon Creole seasoning




2 tablespoons olive oil




$\frac{1}{4}$ cup chopped onion




$\frac{1}{4}$ cup chopped green bell pepper




$\frac{1}{4}$ cup chopped celery




2 tablespoons chopped garlic




$\frac{1}{2}$ cup chopped tomatoes




3 bay leaves




1 teaspoon worcestershire sauce




1 teaspoon hot sauce




¾ cup rice




3 cups chicken stock




5 ounces Andouille sausage, sliced




Salt and pepper




Directions:




In a bowl combine shrimp, chicken and Creole seasoning and work in seasoning well. In a large




saucepan heat oil over high heat with onion, pepper and celery, 3 minutes. Add garlic, tomatoes,




bay leaves, Worcestershire and hot sauces. Stir in rice and slowly add broth. Reduce heat to




medium and cook until rice absorbs liquid and becomes tender, stirring occasionally, about 15




minutes. When rice is just tender add shrimp and chicken mixture and sausage. Cook until meat is




done, about 10 minutes more. Season to taste with salt, pepper and Creole seasoning.







\newpage
Slow cooker Chicken Paprikash




Ingredients:




3 tablespoons all purpose flour




2 pounds boneless, skinless chicken breasts, rinsed and patted dry, then cut into $\frac{1}{2}$ inch strips




1 $\frac{1}{4}$ cups chicken stock




8 ounces mushrooms, sliced




1 large onion, chopped




1 cup chopped red bell pepper




$\frac{1}{2}$ cup shredded carrot




2 large garlic cloves, minced




2 tablespoons Hungarian sweet paprika




1 teaspoon salt




1 teaspoon freshly ground black pepper




1 $\frac{1}{4}$ cups sour cream




Directions:




In a bowl, combine the flour and chicken, tossing well to coat.




In a slow cooker, combine the chicken mixture, stock, mushrooms, onion, bell pepper, carrot,




garlic, paprika, salt and pepper. Cover and cook on low heat for 8 hours. Just before serving, stir in




the sour cream.




Serve with egg noodles, mashed potatoes or orzo.







\newpage
Chicken Marsala




(Mom's recipe)




Ingredients:




1 pound thin chicken




¾ cup Italian bread crumbs




$\frac{1}{2}$ cup milk




1 egg




8 ounces mushrooms




1 small onion, diced




2 tablespoons olive oil




2 tablespoons butter




1 cup marsala




$\frac{1}{2}$ tablespoon of rosemary




Directions:




Heat olive oil in skillet over medium heat.




In a small bowl, beat egg and add milk. In another small bowl or small plate, add bread crumbs.




Dredge chicken in milk and egg mixture and coat with bread crumbs and put in skillet. When




brown (about 3 to 4 minutes), turn over another 3 to 4 minutes).




Remove chicken from pan and put it on a plate.




Turn up heat to medium high and in skillet melt butter, add mushrooms and onion and cook until




soft several minutes. Add marsala wine and rosemary.




Return chicken to pan, turn down heat back to medium, and cook a couple of minutes on each




side.







\newpage
Spice Molasses Cookies




Ingredients:




¾ cup shortening




1 cup sugar




1 large egg




$\frac{1}{4}$ cup molasses




2 cups flour




1 teaspoon baking powder




1 teaspoon baking soda




$\frac{1}{4}$ teaspoon salt




1 teaspoon ginger




1 teaspoon cinnamon




$\frac{1}{2}$ teaspoon nutmeg




$\frac{1}{4}$ teaspoon cloves




$\frac{1}{4}$ teaspoon allspice




Directions:




Beat shortening at medium speed until fluffy. Gradually add 1 cup sugar beating well. Add egg




and molasses -- mix well.




Combine flour and next 8 ingredients -- mix well.




Add $\frac{1}{4}$ of the flour mixture at a time to the creamed mixture beating until smooth.




Cover and chill 1 hour.




Shape dough into 1 inch balls and roll in additional sugar. Place 2 inches apart on cookie sheets.




Bake at 350 degrees for 9-11 minutes







\newpage
Raspberry Lemon Thumbprint Cookies




(Emeril)




Ingredients:




$\frac{1}{2}$ cup raspberry jam




1 tablespoon Chambord




2 $\frac{1}{4}$ cups all purpose flour




1 teaspoon baking powder




$\frac{1}{4}$ teaspoon salt




2 sticks butter at room temperature




2/3 cup sugar




2 large egg yolks




1 tablespoon finely grated lemon zest




1 tablespoon fresh lemon juice




1 teaspoon pure vanilla extract




Directions:




Preheat oven to 350 degrees. Lightly butter 2 large baking sheets




In a small bowl combine the jam and Chambord. Stir to combine.




In a medium bowl, combine the flour, baking powder and salt and whisk to blend.




In a large bowl using an electric mixer, beat the butter and sugar until light and creamy. Beat in




the egg yolks, lemon zest, lemon juice and vanilla. Add the flour mixture in 2 additions and beat




just until moist clumps form. Gather the dough together into a ball.




Pinch off the dough to form 1 inch balls. Place on the prepared baking sheets, spacing 1 inch apart.




Use your floured index finger or $\frac{1}{2}$ teaspoon measuring spoon to create depressions in the center




of each ball. Fill each indentation with nearly $\frac{1}{2}$ teaspoon of the jam mixture. Bake until golden




brown about 20 minutes.




Transfer the cookies to wire racks and cool completely.







\newpage
Snickerdoodles




Ingredients:




2 $\frac{1}{4}$ cups all purpose flour




1 teaspoon baking soda




$\frac{1}{2}$ teaspoon ground nutmeg




$\frac{1}{2}$ cup (1 stick) plus 1 tablespoon unsalted butter, softened




1 teaspoon vanilla




$\frac{1}{2}$ cup firmly packed light brown sugar




1 cup plus 1 tablespoon granulated sugar




2 large eggs




2 teaspoons ground cinnamon




Directions




Preheat the oven to 350 degrees. Sift the flour, baking soda and nutmeg into a medium bowl.




Combine the butter, vanilla, brown sugar and 1 cup of the granulated sugar in a large bowl. Using




an electric mixer on high speed, beat until light and fluffy. Add the eggs, one at a time, beating on




medium speed after each addition. Stir in the flour mixture. Cover the bowl with plastic wrap and




refrigerate for 30 minutes.




Stir together the remaining granulated sugar and the cinnamon in a small bowl.




Scoop the dough into level tablespoons and roll into balls. Roll the dough balls in the cinnamon




sugar, then arrange 3 inches apart on ungreased baking sheets. Bake until the edges are golden 10




to 12 minutes. Cool on wire racks.







\newpage
Peanut Butter Kisses




Ingredients:




48 Hershey's Kisses




$\frac{1}{2}$ cup shortening




¾ cup creamy peanut butter




1/3 cup sugar




1/3 cup packed light brown sugar




1 egg




2 tablespoons milk




1 teaspoon vanilla




1 $\frac{1}{2}$ cups all purpose floour




1 teaspoon baking soda




$\frac{1}{2}$ teaspoon salt




Granulated sugar




Directions:




Heat oven to 375 degrees. Remove wrappers from chocolates.




Beat shortening and peanut butter in large bowl. Add 1/3 cup granulated sugar and brown sugar;




beat until fluffy. Add egg, milk and vanilla; beat well. Stir together flour, baking soda and salt;




gradually beat into mixture.




Shape dough into 1 inch balls. Roll in sugar, place on ungreased cookie sheet.




Bake 8 to 10 minutes or until lightly browned. Immediately press a chocolate kiss into center of




each cookie. Remove from cookie sheet to wire rack. Cool completely.







\newpage
Apple Cheese Crisp




(Mom's blue ribbon recipe)




Ingredients:




4 cups peeled, sliced apples




1 teaspoon water




$\frac{1}{2}$ teaspoon lemon juice




1 cup flour




$\frac{1}{2}$ cup brown sugar




2 tablespoons sugar




$\frac{1}{4}$ teaspoon cinnamon




$\frac{1}{4}$ teaspoon nutmeg




1 stick butter




1 cup shredded cheddar cheese




Directions:




Sprinkle water and lemon juice over apples in baking dish or pie pan




Combine flour, sugars, spices. Cut in butter until mixture is crumbly. Add cheddar cheese and




sprinkle over apples.




Bake 30 minutes at 350 degrees. Serve warm topped with ice cream or whipped cream







\newpage
Bourbon Peach Cobbler




(Tyler Florence)




Ingredients:




8 peaches, peeled and sliced, about 6 to 8 cups




$\frac{1}{4}$ cup bourbon




¾ cup sugar, plus more for dusting




2 tablespoons corn starch




1 teaspoon ground cinnamon




1-1/2 cups all purpose flour




2 teaspoons baking powder




$\frac{1}{2}$ teaspoon kosher salt




16 tablespoons (2 sticks) cold unsalted butter




¾ cup heavy cream, plus more for brushing




Directions:




Heat the oven to 375 degrees.




In a large bowl add the peaches, bourbon, $\frac{1}{4}$ cup sugar, cornstarch and cinnamon and mix well to




coat the peaches evenly; set aside.




Prepare the dumplings: Into a bowl sift together the flour, $\frac{1}{2}$ cup sugar, baking powder and salt.




Cut 12 tablespoons (1-1/2 sticks) butter into small pieces. Add it to the flour mixture and cut it in




with a pastry blender or your hands until the mixture looks like coarse bread crumbs. Pour in the




cream and mix just until the dough comes together. Don't overwork the dough should be slightly




sticky but manageable.




In a 10 inch cast iron skillet over medium low heat, melt the remaining 4 tablespoons butter. Add




the peaches and cook gently until heated through about 5 minutes. Drop the dough by




tablespoonfuls over the warm peaches. There can be gaps, the dough will puff up and spread out




as it bakes. Brush the top with some heavy cream and sprinkle with some sugar; put it into the




oven on a baking sheet to catch any drips. Cook for 40 to 45 minutes until the top is browned and




the fruit is bubbling.







\newpage
Classic Pound Cake




Ingredients:




4 cups all purpose flour




3 cups sugar




2 cups butter, softened




¾ cup milk




6 large eggs




2 teaspoons vanilla extract




Directions:




Preheat oven to 325 degrees. Place flour, sugar, butter, milk, eggs and vanilla (in that order) in a 4




quart bown of a heavy duty electric stand mixer. Beat at low speed 1 minute, stopping to scrape




down sides. Beat at medium speed 2 minutes.




Pour unto a greased and floured 10 inch tube pan and smooth. Bake for 1 hour and 30 minutes or




until a long wooden pick inserted in center comes out clean. Cool in plan on a wire rack 10




minutes. Remove from pan to wire rack and cool completely (about 1 hour)







\newpage
Honey Spice Cake with Rum Glaze




(Emeril)




Ingredients:




2 and 1/3 cups sifted cake flour




1 $\frac{1}{2}$ teaspoons baking powder




$\frac{1}{2}$ teaspoon baking soda




1 teaspoon ground ginger




1 teaspoon ground cinnamon




$\frac{1}{2}$ teaspoon ground cloves




$\frac{1}{2}$ teaspoon salt




1 $\frac{1}{2}$ sticks unsalted butter




2/3 cup honey




$\frac{1}{2}$ cup sugar




3 large egg yolks




¾ cup plus 2 tablespoons plain yogurt




4 large egg whites




1 $\frac{1}{4}$ cups sifted powdered sugar




1 $\frac{1}{2}$ teaspoons rum




Directions:




Preheat oven to 350 degrees. Grease and flour 1 tube or bundt pan.




Sift the cake flour, baking power, baking soda, ginger, cinnamon, cloves and salt together, then




sift again into a large bowl. In another large bowl, beat the butter with an electric mixer on high




speed until creamy. Gradually add the honey and $\frac{1}{4}$ cup of the sugar to the butter and beat on high




speed until well mixed, 2 to 4 minutes. Beat in the egg yolks, 1 at a time. Beat on low and add the




flour mixture in 3 parts, alternating with the yogurt in 2 parts. Beat until smooth, scraping down




the side of the bowl as necessary. In another large bowl, beat the egg whites until soft peaks form.




Gradually add the remaining $\frac{1}{4}$ cup sugar, beating on high speed, until stiff. Fold the egg whites




into the batter. Pour the batter into the prepared pan and bake until a tester comes up clean 40 to




55 minutes.




Let the cake cool in the pan on a wire rack for 10 minutes and then invert the cake onto the rack




and allow to cool completely.




In a small bowl combine the powdered sugar and sum and still to combine. Mixture should be a




stiff glaze. If the glaze is too thick, thin with a bit of milk. Using a spoon, drizzle the glaze all over




the cake in a radom pattern. Let the cake sit until the glaze has hardened. Serve.







\newpage
Cream Cheese Frosting




Ingredients:




4 tablespoons butter, room temperature




4 ounces cream cheese, room temperature




3 cups confectionery sugar, sifted




1 teaspoon vanilla




1 tablespoon milk




Directions:




Cream butter \& cream cheese, add sugar about $\frac{1}{2}$ cup at a time. Add vanilla and milk.







\newpage
Glazed Pineapple




Ingredients:




4 tablespoons melted butter




$\frac{1}{4}$ cup brown sugar




$\frac{1}{4}$ teaspoon cinnamon




$\frac{1}{4}$ teaspoon vanilla extract




Pinch of salt




Splash of rum




Directions:




Mix melted butter, brown sugar, cinnamon, vanilla extract and rum in a bowl. Slice a pineapple in




half lengthwise (keeping the top attached), then cut each half until 3 long wedges; cut out the core.




Place 2 wedges on a sheet of foil; brush with the spiced butter and fold up. Repeat to make 2 more




packets; grill over medium heat until the pineapple is soft and golden on the bottom, 15 to 20




minutes.







\newpage
Ginger Pear Crisp




Ingredients:




6 pears, peeled and sliced




1 tablespoon finely chopped ginger




$\frac{1}{2}$ cup brown sugar




$\frac{1}{2}$ cup raisons




2 teaspoons cinnamon




2 tablespoons butter, cut into bits




Topping:




$\frac{1}{4}$ cup flour




¾ cup rolled oats




$\frac{1}{4}$ cup brown sugar




$\frac{1}{4}$ cup sugar




1 teaspoon cinnamon




6 tablespoons butter




Directions:




Preheat oven to 350 degrees. Toss first six ingredients together in a bowl. Pour into a buttered




baking dish. Using a fork combine the remaining six ingredients. Spoon topping across pears.




Bake for 30 minutes or until brown and bubbly.







\newpage
Pineapple Upside Down Cake




Ingredients:




2 pounds of fresh pineapple, peeled, cored and cubed




2 $\frac{1}{2}$ cups sugar




1 teaspoon ground cinnamon, in all




1 teaspoon grated nutmeg, in all




1 $\frac{1}{2}$ sticks butter, softened, in all




1 teaspoon baking powder




1 teaspoon baking soda




Pinch of salt




2 whole eggs




1 teaspoon vanilla




1 cup milk




2 $\frac{1}{4}$ cups flour




Directions:




Preheat oven 350 degrees. In a mixing bowl, toss the pineapple with 1 cup of sugar, $\frac{1}{2}$ teaspoon




cinnamon and $\frac{1}{2}$ teaspoon nutmeg. In a hot cast iron skillet, melt $\frac{1}{2}$ stick of butter. Caramelize the




pineapple, about 3 to 5 minutes.




For the batter: In a mixing bowl, cream one cup of the butter and 1 $\frac{1}{2}$ cups of sugar. Stir in the




eggs one at a time. Stir in the baking powder, baking soda, vanilla, $\frac{1}{2}$ teaspoon cinnamon, ½




teaspoon nutmeg and milk. Add the flour and mix well. Pour the cake batter evenly over the




pineapple. Bake for about 40 minutes, or until the cake is golden brown and pulls away slightly




from the edges of the skillet. Cool for about 30 minutes, then invert over a large platter.







\newpage
Chocolate Chip Pie




Ingredients:




Pie:




2 ¾ cups all purpose flour




1 $\frac{1}{2}$ teaspoons salt




1 teaspoon baking soda




1 $\frac{1}{4}$ teaspoons baking powder




1 cup (2 sticks) unsalted butter, softened




1 $\frac{1}{2}$ cups packed brown sugar




$\frac{1}{2}$ cup granulated sugar




3 large eggs




1 tablespoon vanilla extract




3 cups semisweet chocolate chips




2 cups chopped walnuts, optional




Whipped cream:




2 pints (4 cups) heavy cream




$\frac{1}{4}$ cup confectioners sugar




$\frac{1}{4}$ cup miniature semisweet chocolate chips




Directions




Preheat oven to 350 degrees. Grease 2 (9 inch) pie plates; set aside.




In a large bowl, sift together the flour, salt, baking soda and baking powder. In the bowl of an




electric mixer, cream together butter, brown sugar and granulated sugar. Add the eggs, 1 at a time,




beating until incorporated. Beat in the vanilla. Add flour mixture a little at a time and mix until




fully combined. Fold in the 3 cups chocolate chips and if desired the walnuts. Divide the dough




between the prepared pie plates and smooth the tops with a spatula.




Bake about 30 minutes or until pies are golden and slightly firm to the touch but still soft. If the




pies begin to darken too much before they are based through, over with foil and continue baking.




Let pies cool completely on a wire rack.




While the pies cool, whip the cream and confectioners sugar until soft peaks form (tips curl). Fold




in the chocolate chips. Refrigerate whipped cream until ready to use. Spread the whipped cream




over the pies and serve.







\newpage
Christmas Trifle




(Mom's recipe)




Ingredients:




1 pound cake (any flavor), cut into 1 inch cubed size pieces




Filling:




1 quart milk




2 cups sugar




1 teaspoon vanilla




10 large egg yolks, beaten




$\frac{1}{2}$ cup cornstarch




$\frac{1}{2}$ cup water




2 tablespoons unsalted butter




To assemble the triffle:




1 quart heavy cream




$\frac{1}{4}$ cup sugar




1 cup orange flavored liqueur (Grand Marnier)




4-6 pints fresh raspberries




Directions:




Filling: combine the milk, sugar and vanilla in a large heavy bottomed saucepan over mediumhigh heat. Whisk to dissolve the sugar. When the mixture comes to a simmer after 5 minutes, take




1 cup of the milk and sugar mixture and add it to the yolks. Whisk to blend well. Slowly add the




yolks to the milk and sugar mixture in the saucepan, whisking constantly. Cook over medium heat




until it thickens slightly, 4 to 5 minutes, whisking occasionally.




Dissolve the cornstarch in the water. Over medium heat, slowly add this mixture to the saucepan,




whisking constantly for 1 minute. Using a wooden spoon, continue stirring for about 2 minutes.




Add the butter and stir until it is completely melted and the mixture has thickened to a custard,




about 2 minutes.




Pour the mixture into a glass bowl. Cover with plastic wrap, pressing the wrap down on the suface




of the custard to prevent a skin from forming. Cool completely and chill for at least 4 hours.




To assemble the trifle:




Beat the cream with an electric mixer on high speed for about 2 minutes. Add the sugar and beat




until a mixture is thick and forms soft peaks, 1 to 2 minutes. Set aside.




Beat the custard with a wire whisk until it is smooth. Set aside.




Spread out the cubed pound cake evenly on a piece of parchment paper. Drizzle the orange liqueur




over the pound cake.




Spread 1 cup of the cream filling on the bottom of a large, deep glass trifle bowl. Top with a layer




of pound cake. Arrange raspberries on top of the pound cake. Spread 2 cups of the cream on tope




of the raspberries. Tope with more pound cake, then raspberries. Spread another cups of the cream






and top with the remaining pound cake and raspberries. Spread the remaining cream on top of the




raspberries. Mound the whipped cream evening over the top.




Serve immediately or keep chilled until ready to serve.







\newpage
Eggnog pound cake




Ingredients:




1 ¾ cups all-purpose flour




2 teaspoons baking powder




$\frac{1}{2}$ teaspoon salt




$\frac{1}{2}$ teaspoon ground nutmeg




$\frac{1}{2}$ teaspoon cinnamon




1 cup sugar




$\frac{1}{2}$ cup (1 stick) unsalted butter, softened




2 tablespoons dark rum




2 teaspoons vanilla




5 large egg yolks




¾ cup milk




Directions:




Preheat the oven to 350 degrees. Grease and flour a 9x5x3 inch loaf pan. Combine the flour,




baking powder, salt and spices in a small bowl.




Using an electric mixer on low speed, beat the sugar, butter, rum, vanilla and egg yolks in a large




bowl for 60 seconds, scraping the bowl frequently. Increase the speed to high and beat for 5




minutes, scraping the bowl occasionally. Reduce the speed to low and mix in one-third of the flour




mixture, alternating with the milk until just combined. Pour the batter into the prepared pan.




Bake for 50-60 minutes or until a toothpick inserted in the center comes out clean. Cool in the pan




for 10 minutes, remove from the pan and cool completely.







\newpage
Pumpkin Cheesecake with Bourbon Spiked Cream




(Emeril/Mom's changes*)




Ingredients:




1 $\frac{1}{2}$ cups ginger snaps*, crushed into crumbs




1 cup ground pecan pieces




1 stick melted butter




2 lbs cream cheese, softened and cubed




1 cup light brown sugar




6 eggs




$\frac{1}{2}$ cup heavy cream




$\frac{1}{2}$ cup all purpose flour




Pinch salt




$\frac{1}{2}$ teaspoon cinnamon




1 teaspoon vanilla




2 cups pumpkin puree




2 cups sweetened whipped cream




Dash bourbon




1 cup semisweet chocolate sauce, warm




Chocolate sauce:




¾ cup half \& half




1 tablespoon butter




$\frac{1}{2}$ pound semisweet chocolate chips




$\frac{1}{4}$ teaspoon vanilla




Directions:




Preheat oven to 350 degrees




Combine the crumb, ground pecans and butter together. Mix well and press into a 12 inch spring




form pan. In a food processor (or mixer) with the metal blade, mix the cream cheese until smooth.




Add the brown sugar and blend. Add the eggs 1 at a time to thoroughly incorporate into the cheese




mixture. Add the heavy cream. Add the flour, salt, cinnamon and vanilla and blend until smooth.




Add the mashed pumpkin and blend until smooth.




Pour into the prepared pan. Bake 1 hour and 15 minutes or until the cake is set. Remove from the




oven and with a knife loosen the sides from the pan. This will prevent the cake from splitting




down the center. Completely cool the cake before cutting.




Combine the whipped cream and bourbon together, blend well. Garnish each piece of cake with




the Bourbon Whipped cream and a drizzle of chocolate sauce.




Chocolate sauce:




Combine the half and half and butter in a small heavy bottomed saucepan over medium heat. Heat




the mixture until a thin paper like skin appears on the top. Do not boil. Add the chocolate and




vanilla and stir until the chocolate melts and the mixture is smooth. Remove from the heat and let




cool.







\newpage
Apple-Oatmeal Crisp with Irish Whiskey Cream




Ingredients:




1 stick cold unsalted butter, cut into pieces




2 pounds Rome apples, peeled, cored and sliced




2 tablespoons fresh lemon juice




1 cup packed light brown sugar




1 cup all purpose flour




2 tablespoons Irish Whiskey




1 teaspoons cinnamon




$\frac{1}{4}$ teaspoon cardamom




Pinch salt




$\frac{1}{4}$ cup Irish oatmeal




$\frac{1}{4}$ cup toasted, chipped walnut pieces




Irish Whiskey Cream:




1 cup heavy cream




1 tablespoon sugar




2 tablespoons Irish whiskey




Directions:




Preheat the oven to 375 degrees. Lightly butter an 11 by 7 inch baking pan and set aside.




In a large skillet, melt 3 tablespoons of butter over medium-high heat. Add the apples, lemon




juice, $\frac{1}{2}$ cup of the brown sugar and 1 tablespoon of the flour. Stir well and cook for 5 minutes.




Add the whiskey, cinnamon, cardamom and salt, stir well and cook for 1 minute. Remove from




the heat.




In a large bowl combine the remaining flour, oatmeal and remaining $\frac{1}{2}$ cup sugar. Add the




remaining 5 tablespoons of butter and bubbly about 35 to 40 minutes. Seat hot with the Irish




Whiskey cream.




Whip the cream until it begins to form soft peaks. Add the sugar and whiskey and beat until stiff




peaks form. Cover and chill.







\newpage
Graham Banana Pudding




Ingredients:




4 cups half \& half




4 large egg yolks




1 $\frac{1}{2}$ cups sugar




$\frac{1}{4}$ cup cornstarch




$\frac{1}{4}$ teaspoon salt




3 tablespoons butter




2 teaspoons vanilla extract




1 (5 ounce) package graham crackers, divided




4 large ripe bananas, sliced and divided




2 cups whipping cream




2 tablespoons sugar




Directions:




Whisk together first 5 ingredients in a saucepan over low heat; cook whisking constantly 8 to 10




minutes or until thickened. Remove from heat; stir in butter and vanilla. Layer 5 graham crackers,




half of bananas and half of pudding in a 13x9 inch dish. Repeat layers. Cover pudding and chill 6




hours.




Beat whipping cream and 2 tablespoons sugar at medium speed with an electric mixer until soft




peaks form. Spread over pudding. Chill until ready to serve







\newpage
Chocolate Pecan Pie




Ingredients:




$\frac{1}{2}$ (15 ounce) package refrigerated piecrusts




1 $\frac{1}{2}$ cups chopped pecans




1 cup (6 ounces) semisweet chocolate morsels




$\frac{1}{2}$ cup granulated sugar




$\frac{1}{2}$ cup firmly packed brown sugar




1 cup dark corn syrup




$\frac{1}{4}$ cup bourbon




4 large eggs




2 teaspoons cornmeal




$\frac{1}{2}$ teaspoon salt




$\frac{1}{4}$ cup butter




2 teaspoons vanilla




Directions:




Fit piecrust into a 9 inch pieplate according to the package directions; fold edges under and crimp.




Sprinkle chopped pecans and chocolate morsels evenly onto piecrust; set aside.




Combine sugars, corn syrup, and bourbon in a large saucepan; bring to a boil over medium heat.




Cook 3 minutes, stirring constantly




Whisk together eggs and remaining ingredients. Gradually stir about $\frac{1}{4}$ hot mixture into egg




mixture; add to remaining hot mixture, stirring constantly. Pour filling into piecrust.




Bake at 325 degrees for 55 minutes, cool.







\newpage
Cheesecake




Ingredients:




Graham Crust:




1 $\frac{1}{2}$ cups graham cracker crumbs




5 tablespoons unsalted butter




1/3 cup firmly packed brown sugar




Pinch ground cinnamom




Cheesecake Batter:




2 pounds cream cheese, softened




1 1/3 cups sugar




5 large eggs




2 teaspoons vanilla




1 tablespoon lemon juice




$\frac{1}{4}$ teaspoon almond extract




¾ cup sour cream




¾ cup whipped cream







Directions:




Preheat oven to 325 degrees




For Graham crust -- toss graham cracker crumbs, butter, brown sugar and cinnamon together in




bottom of 9 inch springform pan and press firmly into pan bottom.




In a mixer bowl, blend cream cheese with sugar until well blended. Add eggs and next 5




ingredients and blend well, stir on low speed about 5 minutes until totally smooth. Pour into




springform pan and place in oven. Bake until just set, about 60 to 75 minutes.




Turn of the oven, open door and let cool in oven 1 hour before refrigerating 8 hours or preferably




overnight.




Serve with desired topping







\newpage
French Chocolate Silk Pie




Ingredients:




1 prebaked 9 inch pastry shell




4 tablespoons unsalted butter




1 cup coarsely chopped semisweet chocolate




1 (14 ounce) can sweetened condensed milk




$\frac{1}{2}$ cup half and half or light cream




Pinch of salt




2 large eggs




1 teaspoon vanilla




1 tablespoon flour




Directions




Preheat oven to 350 degrees.




In a saucepan melt butter and chocolate together over low heat.




In a medium bowl, whisk condensed milk with warm chocolate butter mixture. Stir in cream, salt,




eggs, vanilla and flour; whisk well.




Spoon filling into baked crust and bake 35 to 40 minutes until edges of pie are lightly golden




brown. Serve warm or chilled with whipped cream, chocolate shavings, vanilla ice cream or hot




fudge sauce.







\newpage
Chocolate Mousse




Ingredients:




3 eggs, separated




1 $\frac{1}{2}$ teaspoon vanilla




$\frac{1}{2}$ teaspoon almond extract




4 (1 ounce) squares, semisweet chocolate melted and cooled slightly




$\frac{1}{2}$ teaspoon cream of tarter




$\frac{1}{2}$ cup sugar




1 cup whipping cream




Directions:




Beat egg yolks, lightly add flavorings and chocolate to egg yolks, stirring well.




Beat egg whites (at room temperature) and cream of tarter at high speed of an electric mixer until




frothy. Gradually add sugar, 1 tablespoon at a time beating until stiff peaks form and sugar




dissolves (2 to 4 minutes). Stir about $\frac{1}{4}$ of the meringue into chocolate mixture, fold remaining




meringue into chocolate mixture.




Beat whipping cream at medium speed of an electric mixer until soft peaks form; fold cream into




chocolate mixture. Cover and chill at least 2 hours.







\newpage
Snowtini




Ingredients:




1 ounce bittersweet chocolate




1 $\frac{1}{2}$ cups ice




3 ounces vanilla vodka




3 ounces chocolate liqueur (Godiva)




3 ounces Irish cream (Baileys)




Directions:




Place the martini glasses on a designated, flat shelf in the freezer for 10 minutes




Use a serrated knife, cut shavings off the block of chocolate and reserve for later




Fill a cocktail shaker with ice. Pour the vodka, chocolate liqueur and Irish cream over the ice. Put




top on the shaker and shake firmly.




Carefully pull out the glasses from the freezer taking care not to get the finger marks on the body




of the glass. Pour into chilled glass. Garnish with chocolate shavings in the middle and serve.







\newpage
Sangria




Ingredients:




1 (750 ml) bottle red wine




$\frac{1}{4}$ cup brandy




$\frac{1}{4}$ cup orange flavored liqueur (Grand marier)




2 tablespoons fresh lime juice




2 tablespoons fresh orange juice




$\frac{1}{4}$ cup sugar




$\frac{1}{2}$ orange, thinly sliced




$\frac{1}{2}$ lemon, thinly sliced




1 apple cored and cut into wedges




1 (750 ml) bottle sparkling water, chilled




Directions:




Combine everything but the sparkling water in a large plastic container or glass pitchers. Cover the




chill completely 1 to 2 hours. When ready to serve, add the sparkling water.







\newpage
White Sangria




Ingredients:




2 (750 ml) bottles white Spanish wine, such as Albarino (Galacia), Viura (Rioja), Verdejo (Rueda)




$\frac{1}{2}$ cup spanish brandy




$\frac{1}{4}$ cup Spanish orange liqueur




1 cup pear juice




$\frac{1}{2}$ cup superfine sugar




$\frac{1}{2}$ cup sliced pear




2 apricots, pit removed and sliced into thin wedges




2 peaches, pit removed and sliced into thin wedges




$\frac{1}{2}$ pound seedless white grapes




1 (750 ml) bottle prosecco, chilled




Directions:




Combine the wine, brandy, orange liqueur, pear juice, and sugar in a large pitcher and stir until the




sugar has dissolved. Add the fruit and stir well to combine. Cover and refrigerate until well




chilled, about 2 hours.




Stir in the Prosecco and serve the sangria in large wine glasses, over ice if desired.







\newpage
Shrimp Boil




Ingredients:




1 bottle of beer (any kind)




2 teaspoons kosher salt




2 lemons, halved




3 bay leaves




1 handful of fresh thyme sprigs




1 head of garlic split horizontally




1 tablespoon old bay seasoning




2 pounds jumbo shrimp with shells




Directions:




Fill a large pot with about 2 quarts of water and bottle of beer. Add salt and squeeze in lemon juice




-- add the lemons. Add herbs, garlic and old bay.




Bring to a boil of medium high heat and simmer for 5 minutes to infuse the water with the




aromatics. Reduce the heat to medium low and put shrimp in. simmer, uncovered for 2 to 3




minutes or until shrimp are bright pink. Drain then transfer to a bowl. Chill thoroughly and then




peel.







\newpage
Shrimp Po'Bubba's




Ingredients:




Uncle Bubba's Fry Mix:




6 cups self-rising flour




1 cup cornmeal




1 teaspoon salt




1 teaspoon pepper




2 pounds, uncooked shrimp, peeled, deveined and butterflied




Salt and freshly ground black pepper




3 eggs




$\frac{1}{4}$ cup water




$\frac{1}{2}$ cup hot sauce




2 cups fry mix




Oil for frying




Directions:




For fry mix, mix ingredients together and store in an airtight container for up to 4 months.




Heat Fryer to 350 degrees.




Lightly sprinkle the shrimp with salt and pepper. In a small bowl mix the eggs, $\frac{1}{4}$ cup water and




hot sauce. Place the fry mix in a shallow dish. Dip each shrimp in the egg mixture and then into




the fry mix.




Place the shrimp in the fryer and fry until golden brown, about 2 minutes. Remove with a strainer




and drain on paper towels for a minute.




Serve on toasted hoagie roll.







\newpage
Batter Fried Grouper Sandwiches




Ingredients:




1 cup all purpose flour




$\frac{1}{4}$ cup cornstarch




1 tablespoon garlic powder




$\frac{1}{2}$ teaspoon pepper




4 (4 ounce) grouper fillets




$\frac{1}{2}$ to ¾ cup buttermilk




4 onion sandwich buns, toasted




Oil for frying




Directions:




Combine first 4 ingredients in a shallow dish. Dredge grouper in flour mixture, dip in buttermilk




and dredge in flour mixture again.




Heat fryer to 350 degrees. Fry fillets in hot oil 5 minutes or until golden; drain on paper towels.




Place each fillet on a bun and add desired toppings.







\newpage
Macaroni and 4 Cheeses




(Emeril Lagasse, 2002)




Ingredients:




4 tablespoons butter, plus 2 tablespoons,




plus 1 tablespoon




4 tablespoons flour




2 cups half \& half




¾ teaspoon salt




$\frac{1}{4}$ teaspoon pepper




$\frac{1}{4}$ teaspoon red hot sauce




8-1/2 ounces graded parmigiano-reggiano or other good quality parmesan cheese (about 2 cups)




1 pound elbow macaroni




$\frac{1}{2}$ teaspoon minced garlic




4 ounces grated cheddar cheese




4 ounces grated fontina cheese




4 ounces grated gruyere cheese




$\frac{1}{4}$ cup fresh bread crumbs




$\frac{1}{2}$ teaspoon essence




Directions:




Grate fontina and gruyere cheese and cheddar if not shredded in package. In large bowl combine




remaining parmesan cheese, cheddar, fontina and gruyere.




Boil pot of water, cook macaroni as directed -- drain in colander and return the macaroni to the pot.




Add 2 tablespoons butter and garlic and stir to combine




Heat 4 tablespoons butter and melt




Add flour and cook 3 minutes whisking until rue develops




Stir in half \& half little by little -- 4 to 5 minutes until it begins to get thick




Season with salt, pepper and hot sauce and add 4 ounces of grated parmesan




Stir until cheese is melted and smooth




Add b\'{e}chamel sauce to the macaroni and stir until well combined.




Using the remaining tablespoon of butter, grease a 3 quart baking dish or casserole and preheat




oven to 350 degrees.




Place one-third of the macaroni in the bottom of the prepared baking dish. Top with one-third of




the mixed cheeses. Top with another third of the macaroni and another third of the cheese mixture.




Repeat with the remaining macaroni and cheese mixture. Sprinkle the bread crumbs and essence




over the top.




Bake for 40 to 45 minutes or until the macaroni and cheese is bubbly and hot and the top is golden




brown. Remove from the oven and let sit 5 minutes before serving.




(For lobser mac and cheese, add 1$\frac{1}{2}$ to 2 lbs of cooked lobster meat)







\newpage
Italian Baked Chicken and Pastina




(Giada De Laurentis/with changes by Mom)




Ingredients:




2 cups pastina pasta (or any small pasta)




2 tablespoons olive oil




1 cup cubed chicken breast




$\frac{1}{2}$ cup diced onion




1 clove garlic, minced




2 (14.5 ounce) cans diced tomatoes (Delmonte diced tomatoes with garlic, basil and olive oil)




(Mom puts them in the blender and chops them to make more of a sauce)




2 cups shredded mozzarella




$\frac{1}{4}$ cup chopped fresh flat leaf parsley




$\frac{1}{2}$ teaspoon kosher salt




$\frac{1}{2}$ teaspoon fresh ground pepper




$\frac{1}{4}$ cup bread crumbs




$\frac{1}{4}$ cup grated parmesan




1 tablespoon butter, plus more for buttering the baking dish




Directions:




Preheat oven to 400 degrees.




Bring a medium pot of salted water to a boil over high heat. Add the pasta and cook until tender,




stirring occasionally about 7-8 minutes. Drain pasta into a large mixing bowl.




Meanwhile put the olive oil in a medium saut\'{e} pan over medium heat. Add the chicken and cook




for 3 minutes. Add the onion and garlic stirring to combine and cook until the onions are soft and




the chicken cooked through, about 5 minutes more. Put the chicken mixture into the bowl with the




cooked pasta. Add the canned tomatoes, mozzarella cheese, parsley, salt and pepper. Stir to




combine. Place the mixture in a buttered 8 by 8 by 2 inch baking dish. Sprinkle the bread crumbs




and parmesan cheese over the top of the pasta mixture. Dot the top with small bits of butter. Bake




until the top is golden brown, about 30 minutes.







\newpage
Penne with Shrimp and Herbed Cream Sauce




(Giada De Laurentis)




Ingredients:




1 pound penne pasta




$\frac{1}{4}$ cup olive oil




1 pound medium shrimp, peeled and deveined




4 cloves garlic, minced




$\frac{1}{2}$ teaspoon kosher salt, plus extra for seasoning




$\frac{1}{2}$ teaspoon freshly ground black pepper, plus extra for seasoning




1 (15 ounce can) chopped tomatoes (Delmonte olive oil, garlic \& basil)




$\frac{1}{2}$ cup chopped fresh basil leaves




$\frac{1}{2}$ cup chopped fresh flat leaf parsley




$\frac{1}{4}$ teaspoon crushed red pepper flakes




1 cup white wine




1/3 cup clam juice




¾ cup whipping cream




$\frac{1}{2}$ cup grated Parmesan




Directions:




Bring to a large pot of salted water to a boil over high heat. Add the pasta and cook until tender.




Drain the pasta and set aside.




In a large skillet, heat the oil over medium high heat. Add the shrimp, garlic, $\frac{1}{2}$ teaspoon of salt,




and $\frac{1}{2}$ teaspoon of pepper. Cook, stirring frequently until the shrimp turn pink and are cooked




through, about 3 minutes. Using a slotted spoon, remove the shrimp from the pan and set aside.




Add the tomatoes, $\frac{1}{4}$ cup basil, $\frac{1}{4}$ cup parsley and the red pepper flakes. Cook for 2 minutes,




stirring constantly. Add the wine, clam juice, and heavy cream. Bring the mixture to a boil.




Reduce the heat to medium-low and simmer for 7 to 8 minutes until the sauce thickens. Add $\frac{1}{4}$




cup of the Parmesan, the cooked shrimp, the cooked pasta and the remaining herbs. Toss together




until all ingredients are coated. Season to taste with salt and pepper.




Transfer the pasta to a large serving bowl. Sprinkle with the remaining cheese and serve.







\newpage
Penne a La Vodka Casserole




(Emeril)




Ingredients:




4 tablespoons extra virgin olive oil




1 pound sweet Italian sausage, cut crosswise into 1 inch slices




1 pound hot Italian sausage, cut crosswise into 1 inch slices




4 cups thinly sliced onions




1 ¾ teaspoons salt




¾ teaspoon freshly ground black pepper




$\frac{1}{4}$ cup thinly sliced fresh basil leaves




1 tablespoon minced garlic




$\frac{1}{2}$ cup vodka




2 (16 ounce) cans crushed whole tomatoes, with their juice




1 teaspoon essence




$\frac{1}{2}$ cup heavy cream




1 tablespoon olive oil




1 pound penne pasta




15 ounces ricotta




1 cup grated parmigaino-reggiano




1 $\frac{1}{2}$ cups grated mozzarella




Directions:




Preheat oven to 350 degrees.




Heat 2 tablespoons extra virgin olive oil in large skillet over high heat. Add the sausage and cook




stirring until browned, 4 to 5 minutes. Add the onions, ¾ teaspoon salt and the black pepper.




Cook, stirring occasionally until the onions are just soft about 4 minutes. Add the basil and garlic




and cook, stirring for 2 minutes. Add the vodka and tomatoes, reduce the heat to medium-low and




simmer, uncovered stirring occasionally for 40 minutes. Add the essence and heavy cream, stir to




mix and simmer for 5 minutes. Remove from the heat.




To cook the pasta, combine 4 quarts water, the 1 tablespoon olive oil and the remaining 1 teaspoon




of salt in the large pot over high heat. Bring to the boil, add the pasta and cook 14-15 minutes.




Remove from the heat and drain well. Combine half of the ricotta cheese and half of the




Parmigiano-Reggiano with the remaining 2 tablespoons extra-virgin olive oil in a large mixing




bowl. Add the pasta and toss to coat evenly. Add the sausage mixture and mix well. Add the




remaining Parmigiano-Reggiano and mix well.




Transfer the mixture to a 9 by 13 inch baking dish. Sprinkle with the mozzarella. Bake until




bubbly and golden about 45 minutes. Remove from the oven. Serve warm.







\newpage
Fettuccine Alfredo




(Mom's recipe)




Ingredients:




6 ounces fettuccine, uncooked




$\frac{1}{4}$ cup butter




2 tablespoons flour




$\frac{1}{2}$ cup half and half




$\frac{1}{2}$ cup water




$\frac{1}{2}$ cup freshly grated Parmesan cheese




2 teaspoons parsley flakes




$\frac{1}{2}$ teaspoon coarsely ground pepper




$\frac{1}{4}$ teaspoon salt




1/8 teaspoon essence




1 glove garlic, minced




Directions:




Cook fettuccine according to package directions, drain.




Melt butter in a heavy saucepan over low heat, add flour whisk for 2 minutes. Gradually add half




and half and water, cook over medium heat, stirring constantly until mixture is thickened and




bubbly. Stir in Parmesan cheese, and remaining ingredients. Toss with fettuccine. Serve




immediately.







\newpage
Manicotti




Ingredients:




Sauce




1 cup all purpose flour




4 eggs




1 tablespoon oil




1 teaspoon salt




1 cup water




2 cups ricotta cheese




2 tablespoons grated parmesan cheese




¾ teaspoon salt




$\frac{1}{4}$ teaspoon pepper




2 eggs




8 ounces mozzarella cheese, coarsely shredded




Directions:




Prepare sauce (add meat if desired).




For pancakes, in a small bowl with mixer at low speed, blend flour, eggs, oil, salt and water at




medium speed, beat 1 minute.




Lighlty brush 7 inch skillet with oil. Over medium high heat, heat skillet.




Pour in about 2 tablespoons pancake batter; tip pan to coat bottom evenly with batter. Cook until




the top is set and dry and underside lightly browned, about 30 seconds. Lift pancake onto waxed




paper. Repeat.




Spoon 1/3 of hot sauce evenly into 1 15 $\frac{1}{2}$ by 10 $\frac{1}{2}$ inch roasting pan.




In medium bowl, mix ricotta cheese, Parmesan cheese, salt, pepper and eggs until well blended.




Add mozzarella and stir. Preheat oven to 375 degrees.




Spoon heaping tablespoon of cheese mixture down center of each pancake, top. Fold pancake




edges over cheese. Arrange filled pancakes seam side down in roasting pan.




Spoon remaining sauce over pancakes. Bake 30 minutes or until sauce is hot and bubbly.







\newpage
Lasagna




Ingredients:




1 pound ground beef




1 small onion, diced




1 28 ounce can tomatoes




1 12 ounce can tomato paste




1 tablespoon sugar




1 $\frac{1}{2}$ teaspoons salt




$\frac{1}{2}$ teaspoon oregano




$\frac{1}{2}$ teaspoon thyme




$\frac{1}{2}$ teaspoon crused red pepper




1 garlic glove




1 bay leaf




16 ounce lasagna noodles




2 eggs




1 15 ounce ricotta cheese




1 16 ounce package mozzarella cheese, shredded




Directions:




In a 5 quart dutch oven over high heat; cook ground beef and onion until pan juices evaporate and




beef is browned. Add tomatoes, their liquid and next 8 ingredients.




Heat mixture to boiling, stirring to break up tomatoes. Reduce heat to low, cover and simmer 30




minutes, stirring mixture occasionally.




Discard bay leaf. Tilt pan and spoon off any fat which accumulates on top of sauce. Cook lasagna




noodles as label directs; drain well in colander.




In 13x9 inch baking dish, arrange half of drained lasagna noodles overlapping to fit. Preheat oven




to 375 degrees.




In a small bowl with spoon, combine eggs and ricotta cheese and spoon one half of this mixture




over lasagna noodles in baking dish.




Sprinkle with one half mozzarella; top with one half sauce. Repeat layers. Bake in oven 45




minutes. Remove from oven and let stand 10 minutes before serving.







\newpage
Pulled Pork BBQ




Ingredients:




1 can Root Beer




BBQ Rub




1/3 bottle of BBQ sauce




2 lbs pork roast (end piece)




Directions




Empty root beer at bottom on crock pot. Sprinkle BBQ rub on pork roast and put it crockpot.




Pour BBQ sauce on top of roast. Cook low for 8 hours or more.







\newpage
Pork Egg Rolls with Sweet and Sour Sauce




(Emeril Lagasse)




Ingredients:




2 tablespoons vegetable oil




1 pound ground pork




$\frac{1}{2}$ cup minced onion




1 tablespoon chopped garlic




1 pound bok choy, shredded




$\frac{1}{2}$ pound medium shrimp, peeled, deveined and chopped




1 tablespoon dark sesame oil




Soy sauce to taste




$\frac{1}{4}$ cup sake (optional)




1 tablespoon sugar




1 pound fresh bean sprouts, washed and patted dry




$\frac{1}{4}$ cup green onions, green part only




20 (6 inch) egg roll wrappers




1 egg beaten for egg wash




Oil for frying




Directions:




Preheat the fryer




In a wok, heat the oil. When the oil is hot, add the pork. Season with salt and pepper. Stir fry for 3




minutes. Add the onions and garlic, continue to cook for 2 minutes. Add the bok choy and shrimp.




Season with salt and pepper. Stir-fry for 1 minute. Season with the sesame oil, soy sauce, sake and




sugar. Add the sprouts and green onions and mix thoroughly. Remove from the heat and cool




completely.




To assemble, spoon about $\frac{1}{4}$ cup of the filling in a rectangular shape on the center of each




wrapper. Fold in the ends toward the center about $\frac{1}{4}$ inch. Then, beginning at the bottom roll up




the wrapper, like a jelly roll, using a little of the egg wash to seal the end tightly. Repeat until all




of the egg rolls are done.




Fry the egg rolls in batches until golden brown stirring occasionally for overall browning, about 2




to 3 minutes. Remove from the oil and drain on paper towels. Season with essence. Serve warm




with sweet and sour sauce.







\newpage
Asian Pork Tenderloin




Ingredients:




$\frac{1}{2}$ cup soy sauce




$\frac{1}{4}$ cup pineappled juice




$\frac{1}{4}$ cup coarsely chopped green onions




$\frac{1}{4}$ cup coarsely chopped shallots




2 tablespoons coarsely chopped fresh ginger




2 tablespoons honey




2 tablespoons rice wine vinegar




1 tablespoon essence




$\frac{1}{2}$ teaspoon cinnamon




$\frac{1}{2}$ teaspoon nutmeg




2 tablespoons chopped garlic




1 tablespoon sesame oil




1 tablespoon crushed red pepper




2 pork tenderloins (about 2 pounds)




Directions:




Combine all the ingredients except the tenderloins in a food processor and pulse several times to




puree. Put the tenderloins in a large plastic bag and pour in the marinade. Seal the bag and




refrigerate for 1 hour.




Preheat the oven to 400 degrees.




Heat a large nonstick skillet over high heat. When the skillet is hot, add the tenderloins and sear,




turning to ensure even browning, about 4 minutes. Transfer to a oven safe dish oiled with olive oil




and put in oven and cook for 30 minutes or until an instant-read thermometer reads 145 degrees.




Remove from the oven and let rest for 5 minutes.







\newpage
Double Cut Pork Chops with Caramelized Onion Gravy and pecan




Ingredients:
Glazed Sweet Potatoes




(Emeril)




For the caramelized onion gravy:




2 tablespoons butter




3 cups thinly sliced onions




1 tablespoon light brown sugar




1 teaspoon garlic




1 teaspoon thyme leaves




2 tablespoons all-purpose flour




1 cup chicken stock




Salt \& pepper




For the Pecan Glazed Sweet Potatoes:




1 $\frac{1}{2}$ pounds sweet potatoes




1 tablespoon olive oil




Salt and pepper




6 tablespoons butter




$\frac{1}{2}$ cup light brown sugar




$\frac{1}{2}$ cup pecans




For the pork chops:




4 double cut bone in pork chops




1 tablespoon essence




2 teaspoons salt




2 tablespoons olive oil.




Directions:

Gravy:




In a small saucepan set over medium heat, add the butter. Once melted, add the onions and sugar




to the pan and sweat, stirring occasionally until wilted and well caramelized, about 18 to 20




minutes. Add the garlic and thyme to the pan and saut\'{e} until fragrant, about 30 seconds. Add the




flour to the pan and stir to make a roux, about 2 to 3 minutes. Add the chicken stock. Bring to a




boil and reduce heat to a simmer. Simmer the gravy for 15 minutes and season with the salt and




pepper.




Sweet potatoes:




Wash the sweet potatoes and peel. Chop the sweet potatoes into 1 inch pieces and place in a




roasting pan. Drizzle with the olive oil and season with the salt and pepper. Place the potatoes in




the oven and roast until tender about 30 minutes. Remove from the oven and set aside. In a large




12 inch saut\'{e} pan, add the butter and brown sugar. When the butter begins to boil with the sugar,




add the pecans and the sweet potatoes. Continue to cook, tossing occasionally, until the potatoes




are well glazed, about 3 minutes.







For the Pork chops:




Preheat the oven to 400 degrees. Set a large 12inch saut\'{e} pan over medium-high heat. Add the




olive oil to the pan and once hot, place the pork chops in the pan. Sear the pork chops until well




caramelized about 5 minutes. Turn over and sear on the second side for an additional 5 minutes.




Remove the pan from the stovetop and place in the oven. Roast the pork chops until a thermoter




reaches 150 degrees about 10 to 12 minutes for medium. Remove the chops from the oven and




serve with the glazed sweet potatoes and the caramelized onion gravy. Garnish with chopped




parsley.







\newpage
Pork Chops, Cabbage and Apples




Ingredients:




3 teaspoons paprika, divided




2 teaspoons chopped fresh or 1 teaspoon dried thyme, divided




2 teaspoons kosher salt, divided




1 $\frac{1}{2}$ teaspoon chopped fresh or 1 teaspoon dried sage, divided




6 (1/2 inch thick) pork loin chops




2 bacon slices




1 head cabbage coarsely chopped




2 medium onions, thinly sliced




1 large Granny Smith apple, peeled and sliced




1 tablespoon tomato paste




1 (12 ounce) bottle lager beer




Directions:




Combine 2 teaspoons paprika, 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried thyme, 1 teaspoon salt, 1




teaspoon pepper and 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried sage, rub evenly overly pork chops.




Cook bacon slices in large, deep skillet over medium high heat 6 to 8 minutes or until crisp;




remove bacon and drain on paper towels, reserving drippings in skillet. Crumble bacon.




Cook pork in hot drippings 3 minutes on each side or until browned and done; remove pork from




pan and keep warm.




Add cabbage, onions and apple to pan. Cover and reduce heat to medium; cook stirring




occasionally 15 minutes or until cabbage begins to wilt. Add tomato paste, beer, bacon remaining




1 teaspoon paprika, 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried thyme, 1 teaspoon salt, $\frac{1}{2}$ teaspoon




pepper and 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried sage, stirring to loosen particles from bottom of




skillet. Cover and cook 15 minutes or until cabbage is tender and liquid is slightly thickened. Add




pork, and cook uncovered 5 minutes or until thoroughly heated.







\newpage
Sugarcane Baked Ham with Spiced Apples and Pears




Ingredients:




12 sugarcane swizzle sticks, each cut into about 3 inch pieces




1 hickory smoked ham, spiral sliced, 8 to 10 pounds (no bone, water added, cooked)




1 $\frac{1}{2}$ pound (about 4) Granny Smith apples




1 $\frac{1}{2}$ pound (about 4) Bartlett pears




Glaze:




1 cup firmly packed light brown sugar




1 cup Steens 100 percent Pure Cane Syrup




$\frac{1}{2}$ cup dark molasses




$\frac{1}{2}$ cup dark corn syrup




1/8 teaspoon freshly grated nutmeg




$\frac{1}{4}$ teaspoon ground cloves




1/8 teaspoon ground allspice




$\frac{1}{2}$ teaspoon ground cinnamon




1 teaspoon dried mustard




$\frac{1}{4}$ cup water




Directions:




Preheat oven to 350 degrees




Line a shallow baking pan with parchment or waxed paper. Insert the sugarcane sticks into the




ham at 3 to 4 inch intervals. Tie the ham, using kitchen twine, horizontally and vertically, like a




package to hold it together. Place it on a wire rack in the baking pan.




In a mixing bowl, combine all the glaze ingredients together except for the mustard and water.




Mix well. In a small bowl, dissolve the mustard in the water, then add to the spice mixture. Blend




well.




Brush the entire ham with the glaze, coating it evenly. Wash, core and halve the fruit. Place all




around the ham. Baste the ham a second time and baste the fruit with the glaze. Bake for 45




minutes. Baste the ham and fruit again. Bake another 45 minutes. Remove the ham from the oven




and let is rest for 5 minutes. Remove and discard the string and swizzle sticks. Serve the apples




and pears on a platter with the ham. Serve everything warm or at room temperature.







\newpage
French Dressing




(Grandma's recipe)







Ingredients:




$\frac{1}{4}$ cut vinegar




$\frac{1}{2}$ cup sugar




1 teaspoon dry mustard




1 teaspoon salt




1 teaspoon paprika




1 cup olive oil




Directions:




Beat 3 minutes slowly add oil. Beat 3 more minutes.







\newpage
Sweet and Sour Sauce




Ingredients:




1 tablespoon vegetable oil




$\frac{1}{2}$ medium onion, chopped




$\frac{1}{2}$ teaspoon grated ginger




$\frac{1}{4}$ cup finely diced pineapple




1/3 cup rice vinegar




$\frac{1}{4}$ cup ketchup




2 tablespoons chili garlic sauce




$\frac{1}{4}$ cup sugar




$\frac{1}{4}$ cup chicken broth




2 teaspoons cornstarch




Directions:




Heat the oil in a small saucepan over medium high heat. When hot, add the onions and cook,




stirring until softened about 2 minutes. Add the ginger and cook, stirring constantly for 30




seconds. Stir in the pineapple, vinegar, ketchup, chili garlic sauce and the sugar. Bring the sauce to




s simmer and cook stirring for 3 minutes. In a small bowl, whisk together the chicken broth and




cornstarch until smooth. Add to the sauce mixture and bring to a boil. Cook for 1 minute, remove




from the heat and cool slightly.







\newpage
Bearnaise Sauce




Ingredients:




3 tablespoons white wine vinegar




3 tablespoons dry white wine




10 peppercorns, crushed




3 shallots, finely chopped




1 tablespoon chopped fresh tarragon




1 tablespoon water




3 egg yolks




$\frac{1}{4}$ teaspoon salt




Pinch of ground red pepper




¾ cup unsalted butter, melted and cooled




1 tablespoon chopped fresh chervil or parsley




Directions:




Bring the first 5 ingredients to a boil over medium high heat, and cook whisking constantly until




mixture is reduced to 1 tablespoon. Remove from heat and whisk in water and next 3 ingredients.




Cook over low heat, whisking constantly 4 minutes or until pale yellow. Remove from heat; add




butter in slow, steady stream, whisking constantly until thickened.




Pour sauce through a wire mesh strainer into a bowl, discarding shallot; stir in chervil and serve




warm with steak







\newpage
Roasted Pear-Butternut Soup with Crumbled Stilton




Ingredients:




2 ripe pears, peeled, quartered and cored




2 pounds butternut squash, peeled, seeded and cut into 2 inch chunks




2 medium tomatoes, cored and quartered




1 large leek, pale green and white parts only, halved lengthwise, sliced and washed thoroughly




2 cloves garlic crushed




2 tablespoons extra-virgin olive oil




$\frac{1}{2}$ teaspoon salt




Freshly ground pepper




4 cups vegetable broth




2/3 cup crumbled Stilton or other blue cheese




1 tablespoon thinly sliced fresh chives




Directions:




Preheat oven to 400 degrees.




Combine pears, squash, tomatoes, leek, garlic, oil, $\frac{1}{4}$ teaspoon salt and pepper in a large bowl; toss




to coat. Spread evenly on a large rimmed baking sheet. Roast, stirring occasionally, until the




vegetables are tender, 40 to 55 minutes. Let cool slightly.




Place half the vegetables and 2 cups broth in a blender, puree until smooth. Transfer to a large




saucepan. Puree the remaining vegetables and 2 cups broth. Add to the pan and stir in the




remaining $\frac{1}{4}$ teaspoon salt.




Cook the soup over medium low heat, stirring until hot, about 10 minutes. Divide among 6 bowls




and garnish with cheese and chives.







\newpage
Smoked Turkey Monte Cristo Sandwiches




Ingredients:




4 tablespoons whole grain mustard




8 honey wheat bread slices




$\frac{1}{2}$ pound thinly sliced smoke deli turkey




4 swiss or mozzarella cheese slices




2 large eggs




1/3 cup milk




2 tablespoons butter




2 tablespoons blackberry preserves




1 tablespoon powdered sugar




Directions:




Spread mustard over 1 side of each bread slice. Layer 4 bread slices, mustard side up with turkey




and cheese slices. Top with remaining bread slices, mustard sides down.




Whisk together eggs and milk in a shallow dish. Dip both sides of each sandwich into egg mixture.




Melt 1 tablespoon butter in a large nonstick skillet over medium heat; cook 2 sandwiches in skillet




3 to 4 minutes on each side or until lightly browned. Repeat procedure with remaining butter and




sandwiches. Serve immediately with blackberry preserves. Dust with powdered sugar.









\end{document}
