\newrecipe
\begin{recipe}
[
preparationtime = {\unit[3.5]{h}},
bakingtime = {\unit[30]{m}},
portion = {\portion{1}}
]
{Foccacia with Savory Olives}

\ingredients{
1 $\frac{1}{2}$ cups warm water\\ 
1 tablespoon sugar\\ 
2 (1/4 ounce) packages active dry yeast\\ 
3 $\frac{1}{2}$ cups all purpose flour\\ 
2 teaspoons kosher salt\\ 
6 tablespoons extra-virgin olive oil, divided\\ 
1/3 cup black olives, sliced\\ 
$\frac{1}{4}$ cup slivered or sliced almonds\\ 
2 tablespoons chopped fresh savory\\ 
Coarse sea salt and freshly ground pepper
}

\preparation{
\step In a small bowl, dissolve the sugar in the warm water. Sprinkle the yeast over the water and let stand for 10 minutes.
\step In the bowl of a mixer fitted with a paddle attachment, add 3 cups of the
flour, the salt, 2 tablespoons of the olive oil and the yeast mixture. 
\step Turn the mixer on low speed and slowly mix until the dough comes together. 
\step Gradually add remaining flour. If the dough seems too wet, add up to $\frac{1}{4}$ cup more flour. 
\step Place the dough into an oiled bowl, cover and let rise in a warm place, free from drafts for 3 hours.
\step Preheat the oven to 375 degrees.\\ 
\step Punch down the dough and transfer onto a lightly greased 9 by 13 inch baking sheet. Spread the dough to the edges of the baking sheet. Using your fingertips make dimples in the dough.
\step Drizzle the dough with the 2 tablespoons of the olive oil and sprinkle with the olives, almonds and savory.
\step Sprinkle lightly with salt and pepper. Then, bake for 30 to 35 minutes or until golden brown.
\step Drizzle with remaining 2 tablespoons of high quality olive oil.
}
\end{recipe}