\newrecipe
\begin{recipe}
[
preparationtime = {\unit[35]{m}},
bakingtime = {\unit[3]{h}},
portion = {\portion{4-6}},
]
{Beef and Guinness Stew}

\ingredients{
2 pounds stewing beef\\ 
3 tablespoons oil\\ 
2 tablespoons flour\\ 
Salt and freshly ground black pepper\\ 
Pinch of cayenne\\ 
2 large onions, coarsely chopped\\ 
1 garlic clove, crushed\\ 
2 tablespoons tomato puree\\ 
%, dissolved in 4 tablespoons water
1 $\frac{1}{4}$ cups Guinness\\ 
2 cups largely diced carrots\\ 
Sprig of fresh thyme\\ 
Chopped parsley, for garnish\\ 
}

\preparation{
\step Trim the meat of any fat or gristle and cut into 2 inch cubes. Toss beef with 1 tablespoon of the oil.
\step In a small bowl, season the flour with salt, pepper and cayenne. Toss meat with seasoned flour.
\step Heat remaining 2 tablespoons oil in a large skillet over high heat. Brown the meat on all sides.
\step Dissolve the tomato puree into 4 tablespoons of water, mixing well. 
\step Reduce the heat, add the onions, crushed garlic and tomato puree to the skillet, cover and cook gently for 5 minutes.
\step Transfer the contents of the skillet to a casserole and pour half of the Guinness into the skillet. 
\step Bring Guinness to a boil and stir to dissolve the caramelized meat juices on the pan.
\step Pour over the meat, along with the remaining Guinness. Add the carrots and thyme.\\ 
\step Stir and adjust seasonings. Cover the casserole and simmer over low heat or in a 300 degree oven until the meat is tender 2 to 3 hours. 
\step Garnish the beef with parsley.
}
\end{recipe}
