\newrecipe
\begin{recipe}
[
preparationtime = {\unit[50]{m}},
portion = {\portion{4}},
]
{Lasagna Soup}

\ingredients{
Kosher salt\\ 
8 ounces lasagna noodles (about 10 noodles)\\ 
1 tablespoon extra virgin olive oil\\ 
%plus more for drizzling
1 onion, chopped\\ 
$\frac{1}{2}$ pound sweet Italian sausage, casing removed\\ 
3 cloves garlic, chopped\\ 
1 teaspoon dried oregano\\ 
2 tablespoons tomato paste\\ 
4 cups low sodium chicken broth\\ 
1 15 ounce can crushed tomatoes\\ 
$\frac{1}{2}$ cup chopped fresh basil\\ 
Extra basil leaves for topping\\ 
$\frac{1}{3}$ cup grated parmesan cheese\\ 
$\frac{1}{4}$ cup heavy cream or half and half\\ 
Ricotta cheese for topping\\ 
}

\preparation{
\step Bring a large pot of salted water to a boil. While waiting, break lasagna noodles into pieces.
\step Add the noodles and cook as the label directs. Drain, drizzle with the olive oil and toss.
\step Heat 1 tablespoon olive oil in a large dutch oven or heavy bottomed pot over medium high heat.
\step Add the onion and cook stirring until softened about 4 minutes.
\step Add the sausage, garlic and oregano and cook, stirring and breaking up the sausage with a wooden spoon until the sausage is browned, about 3 minutes.
\step Add the tomato paste and cook stirring until darkened about 2 minutes.
\step Add the chicken broth, tomatoes, and 1 cup water, cover and bring to a simmer.
\step Uncover and cook until slightly reduced about 10 minutes.
\step Stir in the noodles, basil, parmesan and heavy cream, simmer 2 more minutes.\\ 
\step Divide the soup among bowls. Top with ricotta and sliced basil.
}
\end{recipe}