\newrecipe
\begin{recipe}
[
preparationtime = {\unit[40]{m}},
bakingtime = {\unit[55]{m}},
portion = {\portion{4-6}},
]
{Roasted Pear-Butternut Soup with Crumbled Stilton}

\ingredients{
2 ripe pears\\ 
%, peeled, quartered and cored\\ 
2 pounds butternut squash\\ 
%, peeled, seeded and cut into 2 inch chunks\\ 
2 medium tomatoes, cored and quartered\\ 
1 large leek\\ 
%, pale green and white parts only, halved lengthwise, sliced and washed thoroughly
2 cloves garlic crushed\\ 
2 tablespoons extra-virgin olive oil\\ 
$\frac{1}{2}$ teaspoon salt\\ 
Freshly ground pepper\\ 
4 cups vegetable broth\\ 
$\frac{2}{3}$ cup crumbled Stilton or blue cheese\\ 
1 tablespoon thinly sliced fresh chives\\ 
}

\preparation{
\step Preheat oven to 400 degrees. Then peel, core, and quarter the pears.
\step De-seed the butternut squash, peel and cut it into 2 inch chunks.
\step Take only the pale green and white parts of the leek, half lengthwise, slice and washed thoroughly.
\step Combine pears, squash, tomatoes, leek, garlic, oil, $\frac{1}{4}$ teaspoon salt and pepper in a large bowl; toss to coat.
\step Spread the mixture evenly on a large rimmed baking sheet. Roast, stirring occasionally, until the vegetables are tender, 40 to 55 minutes. Let cool slightly.
\step Place half the vegetables and 2 cups broth in a blender, puree until smooth. Transfer to a large saucepan.
\step Puree the remaining vegetables and 2 cups broth. Add to the pan and stir in the remaining $\frac{1}{4}$ teaspoon salt.
\step Cook the soup over medium low heat, stirring until hot, about 10 minutes. Divide among 6 bowls and garnish with cheese and chives.
}
\end{recipe}
