\newrecipe
\begin{recipe}
[
preparationtime = {\unit[30]{m}},
bakingtime = {\unit[1.5]{h}},
portion = {\portion{4-6}},
source = Giada De Laurentiis
]
{Braciole}

\ingredients{
$\frac{1}{2}$ cup dried Italian style bread crumbs\\ 
1 garlic clove, minced\\ 
2/3 cup grated Pecorino Romano\\ 
1/3 cup grated provolone\\ 
2 tablespoons fresh Italian parsley leaves\\ 
4 tablespoons olive oil\\ 
Salt and freshly ground pepper\\ 
1 (1 $\frac{1}{2}$ pound) flank steak\\ 
1 cup dry white wine\\ 
3 $\frac{1}{4}$ cups marinara sauce\\ 
}

\preparation{
\step Chop the parsley leaves finely. Preheat the oven to 350 degrees.
\step Stir the first 5 ingredients (bread crumbs, garlic, Pecorino Romano, provolone, and parsley) in a medium bowl to blend. Stir in 2 tablespoons of the oil.
\step Season the mixture with salt and pepper and set aside.
\step Lay the flank steak flat on the work surface. Sprinkle the bread crumb mixture evenly over the steak to cover the top evenly.
\step Starting at 1 short end, roll up the steak as a jelly roll to enclose the filling completely. 
\step Using butcher's twine, tie the steak roll to secure. Sprinkle the braciole with salt and pepper.
\step Heat the remaining 2 tablespoons of oil in a heavy large ovenproof skillet over medium heat.
\step Add the braciole and cook until browned on all sides, about 8 minutes.\\ 
\step Add the wine to the pan and bring to a boil.\\ 
\step Stir in the marinara sauce. Cover partially with foil and bake until the meat is almost tender, turning the braciole and basting with the sauce every 30 minutes.
\step After 1 hour, uncover and continue baking until the meat is tender, about 30 minutes longer. The total cooking time should be about 1 $\frac{1}{2}$ hours.
\step Remove the braciole from the sauce. Using a large sharp knife, cut the braciole crosswise and diagonally into $\frac{1}{2}$ inch thick slices.
\step Transfer the slices to plates. Spoon the sauce over and serve.
}
\end{recipe}
