\newrecipe
\begin{recipe}
[
preparationtime = {\unit[3]{h}},
bakingtime = {\unit[1.25]{h}},
portion = {\portion{4-6}},
]
{French Dip Sandwiches}

\ingredients{
\textbf{For the onion spread:}\hspace*{\hfill}\\ 
3 tablespoons vegetable oil\\ 
1 large onion, thinly sliced\\ 
kosher salt\\ 
6 medium shallots, thinly sliced\\ 
2 bunches scallions, chopped\\ 
%(white and green parts separated)
1-$\frac{1}{2}$ cups sour cream\\ 
1 cup mayonnaise\\ 
2 teaspoons white wine vinegar\\ 
2 teaspoons Worcestershire sauce\\ 
\\ \textbf{For the sandwiches:}\hspace*{\hfill}\\ 
6 cloves garlic\\ 
kosher salt\\ 
1 teaspoon extra-virgin olive oil\\ 
$\frac{1}{2}$ teaspoon celery salt\\ 
pinch of cayenne pepper\\ 
freshly ground black pepper\\ 
3-4 pound beef eye round roast\\ 
4 cups beef broth\\ 
2 stalks celery, roughly chopped\\ 
3 sprigs parsley\\ 
2 tablespoons butter\\ 
2 tablespoons flour\\ 
2 teaspoons dry sherry\\ 
6 6 inch Italian rolls\\ 
12 slices provolone cheese\\ 
}

\preparation{\\ 
\\ \textbf{Make the onion spread:}
\step Heat the vegetable oil in a large skillet over medium low heat. 
\step Add the onion and pinch of salt; cover and cook, stirring, until golden about 35 minutes.
\step Add the shallots and scallion whites; cover and cook stirring until browned about 25 more minutes.
\step Stir in scallion greens, then remove from the heat and let cool.
\step Chop the onion mixture and transfer to a bowl. Add the sour cream, mayonnaise, vinegar, Worcestershire sauce and 1 teaspoon salt. 
\step Cover and refrigerate at least 2 hours and up to 1 day.
\\ 
\\ \textbf{Make the beef for the sandwiches:}
\step Mince the garlic, then sprinkle with 1 teaspoon salt and mash into a paste with the flat side of a large knife.
\step Transfer to a bowl; add the olive oil, celery salt, cayenne and $\frac{1}{2}$ teaspoon black pepper.
\step Cut small slits all over the beef with a knife, then use your fingers and push the garlic paste into the slits.
\step Cover, refrigerate at least 1 hour or overnight.\\ 
\step Preheat the oven to 425 degrees. Bring the beef to room temperature.
\step Sprinkle with 2 teaspoons salt and $\frac{1}{2}$ teaspoon pepper. 
\step Place on a rack in a roasting pan; add 1 cup broth, $\frac{1}{4}$ cup water, the celery, onion, parsley to the pan.
\step Roast 10 minutes, then reduce the oven temperature to 350 degrees and roast until thermometer inserted into the center of the beef registers 115 degrees about 60 minutes longer.
\step Transfer to a cutting board; let rest 20 minutes. Strain the pan juices; reserve.\\ 
\\ \\ \textbf{Make the jus:}
\step Melt the butter in a medium saucepan over medium heat. Add the flour and cook stirring 1 minute.
\step Whisk in the reserved pan juices and the remaining 3 cups broth and bring to a boil, whisking.
\step Remove the pan from the heat and stir in the sherry.\\ 
\step Split french rolls and put two pieces of provolone cheese on each roll – put in 350 degree oven until the cheese melts.
\step Brush the rolls with some of the onion spread. Thinly slice the beef against the grain.
\step Dunk the slices in the jus, then layer on the rolls. Serve the remaining jus in small bowls for dipping. Remaining onion spread can be used on chips as dip.

}
\end{recipe}
