\newrecipe
\begin{recipe}
[
preparationtime = {\unit[40]{m}},
bakingtime = {\unit[30]{m}},
portion = {\portion{4-6}},
source = Giada De Laurentis with changes by Mom
]
{Italian Baked Chicken and Pastina}

\ingredients{
2 cups pastina pasta (or any small pasta)\\ 
2 tablespoons olive oil\\ 
1 cup cubed chicken breast\\ 
$\frac{1}{2}$ cup diced onion\\ 
1 clove garlic, minced\\ 
2 (14.5 ounce) cans diced tomatoes\\ 
%(Delmonte diced tomatoes with garlic, basil and olive oil)
%(Mom puts them in the blender and chops them to make more of a sauce)
2 cups shredded mozzarella\\ 
$\frac{1}{4}$ cup chopped fresh flat leaf parsley\\ 
$\frac{1}{2}$ teaspoon kosher salt\\ 
$\frac{1}{2}$ teaspoon fresh ground pepper\\ 
$\frac{1}{4}$ cup bread crumbs\\ 
$\frac{1}{4}$ cup grated parmesan\\ 
1$\frac{1}{2}$ tablespoon butter\\ 
}

\hint{Mom recommends using Delmonte diced tomatoes with garlic, basil and olive oil and putting them in the blender to chop them up into more of a sauce.}

\preparation{
\step Preheat oven to 400 degrees. Use $\frac{1}{2}$ tablespoon of the butter to butter a 8x8x2 inch baking dish.
\step Bring a medium pot of salted water to a boil over high heat. Add the pasta and cook until tender, stirring occasionally about 7-8 minutes.
\step Drain pasta into a large mixing bowl.\\ 
\step Meanwhile put the olive oil in a medium saut\'{e} pan over medium heat. Add the chicken and cook for 3 minutes.
\step Add the onion and garlic, stirring to combine and cook until the onions are soft and the chicken cooked through, about 5 minutes more.
\step Put the chicken mixture into the bowl with the cooked pasta. Add the canned tomatoes, mozzarella cheese, parsley, salt and pepper.
\step Stir to combine. Then, place the mixture in the buttered baking dish.\\ 
\step Sprinkle the bread crumbs and parmesan cheese over the top of the pasta mixture. Dot the top with small bits of 1 tablespoon of the butter.
\step Bake until the top is golden brown, about 30 minutes.
}
\end{recipe}
