\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[45]{m}},
portion = {\portion{4-6}},
]
{Lasagna}

\ingredients{
1 pound ground beef\\ 
1 small onion, diced\\ 
1 28 ounce can tomatoes\\ 
1 12 ounce can tomato paste\\ 
1 tablespoon sugar\\ 
1 $\frac{1}{2}$ teaspoons salt\\ 
$\frac{1}{2}$ teaspoon oregano\\ 
$\frac{1}{2}$ teaspoon thyme\\ 
$\frac{1}{2}$ teaspoon crushed red pepper\\ 
1 garlic glove\\ 
1 bay leaf\\ 
16 ounce lasagna noodles\\ 
2 eggs\\ 
15 ounce ricotta cheese\\ 
16 ounce shredded mozzarella cheese\\ 
}

\preparation{
\step In a 5 quart dutch oven over high heat, cook ground beef and onion until pan juices evaporate and beef is browned.
\step Add tomatoes, their liquid and next 8 ingredients (tomato paste, sugar, salt, oregano, thyme, red pepper, garlic, and bay leaf).
\step Heat mixture to boiling, stirring to break up tomatoes. Reduce heat to low, cover and simmer 30 minutes, stirring mixture occasionally.
\step Discard bay leaf. Tilt pan and spoon off any fat which accumulates on top of sauce.
\step Cook lasagna noodles as label directs; drain well in colander.
\step In 13x9 inch baking dish, arrange half of drained lasagna noodles overlapping to fit. 
\step Preheat oven to 375 degrees.\\ 
\step In a small bowl with spoon, combine eggs and ricotta cheese and spoon one half of this mixture over lasagna noodles in baking dish.
\step Sprinkle with one half mozzarella; top with one half sauce. Repeat layers. Bake in oven 45 minutes. 
\step Remove from oven and let stand 10 minutes before serving.
}
\end{recipe}
