\begin{recipe}
[
preparationtime = {\unit[40]{m}},
bakingtime = {\unit[40]{m}},
portion = {\portion{5-7}},
source = Emeril Lagasse
]
{Macaroni and 4 Cheeses}

\ingredients{
7 tablespoons butter\\ 
4 tablespoons flour\\ 
2 cups half \& half\\ 
$\frac{3}{4}$ teaspoon salt\\ 
$\frac{1}{4}$ teaspoon pepper\\ 
$\frac{1}{4}$ teaspoon red hot sauce\\ 
8-1/2 ounces graded parmigiano-reggiano\\ 
1 pound elbow macaroni\\ 
$\frac{1}{2}$ teaspoon minced garlic\\ 
4 ounces grated cheddar cheese\\ 
4 ounces grated fontina cheese\\ 
4 ounces grated gruyere cheese\\ 
$\frac{1}{4}$ cup fresh bread crumbs\\ 
$\frac{1}{2}$ teaspoon essence\\ 
}

\hint{Make sure to use good quality cheese, especially the parmesan and cheddar, I like to use a good white cheddar. Gruyere can be substituted with other high quality swiss cheeses and fontina can be substituted as well according to taste.\\ 
For lobser mac and cheese, add 1$\frac{1}{2}$ to 2 lbs of cooked lobster meat (or any other type of meat can be added).}

\preparation{
\step Grate fontina, gruyere cheese, cheddar, and parmigiano-reggiano (keep 4 ounces of this separate.
\step  In large bowl combine remaining parmesan cheese (4.5 ounces), cheddar, fontina, and gruyere.
\step Boil pot of water, cook macaroni as directed -- drain in colander and return the macaroni to the pot.
\step Add 2 tablespoons butter and fresh chopped garlic to the macaroni and stir to combine.
\step In a separate pot, heat 4 tablespoons butter and melt then add flour and cook 3 minutes whisking until a white roux develops.
\step Stir in half \& half little by little -- 4 to 5 minutes until it begins to get thick, creating a b\'echamel sauce.
\step Season b\'echamel sauce with salt, pepper and hot sauce and add 4 ounces of grated parmesan that was set aside. Stir until cheese is melted and smooth
\step Add b\'{e}chamel sauce to the macaroni and stir until well combined.\\ 
\step Using the remaining tablespoon of butter, grease a 3 quart baking dish or casserole and preheat oven to 350 degrees.
\step Place one-third of the macaroni in the bottom of the prepared baking dish. Top with one-third of the mixed cheeses.
\step Top with another third of the macaroni and another third of the cheese mixture.\\ 
\step Repeat with the remaining macaroni and cheese mixture. Sprinkle the bread crumbs and essence over the top.
\step Bake for 30 to 45 minutes or until the macaroni and cheese is bubbly and hot and the top is golden brown. Remove from the oven and let sit 5 minutes before serving.
% (For lobser mac and cheese, add 1$\frac{1}{2}$ to 2 lbs of cooked lobster meat)
}
\end{recipe}
