\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[30]{m}},
portion = {\portion{4-5}},
]
{Manicotti}

\ingredients{
Sauce\\ 
1 cup all purpose flour\\ 
4 eggs\\ 
1 tablespoon oil\\ 
1 teaspoon salt\\ 
1 cup water\\ 
2 cups ricotta cheese\\ 
2 tablespoons grated parmesan cheese\\ 
$\frac{3}{4}$ teaspoon salt\\ 
$\frac{1}{4}$ teaspoon pepper\\ 
2 eggs\\ 
8 ounces mozzarella cheese, coarsely shredded\\ 
}

\preparation{
\step Prepare marinara sauce (add meat if desired).\\ 
\step For manicotti noodles, in a small bowl with mixer at low speed, blend flour, eggs, oil, salt and water at medium speed, beat 1 minute.
\step Lighlty brush 7 inch skillet with oil. Over medium high heat, heat skillet.
\step Pour in about 2 tablespoons  batter; tip pan to coat bottom evenly with batter. Cook until the top is set and dry and underside lightly browned, about 30 seconds. Lift noodle onto waxed paper. Repeat.
\step Spoon 1/3 of hot sauce evenly into 1 15 $\frac{1}{2}$ by 10 $\frac{1}{2}$ inch roasting pan.
\step In medium bowl, mix ricotta cheese, Parmesan cheese, salt, pepper, and eggs until well blended.
\step Add mozzarella and stir. Then preheat oven to 375 degrees.\\ 
\step Spoon heaping tablespoon of cheese mixture down center of each noodle.\\ 
\step Fold noodle edges over cheese to form manicotti. Arrange filled noodle seam side down in roasting pan.
\step Spoon remaining sauce over noodles. Bake 30 minutes or until sauce is hot and bubbly.
}
\end{recipe}
