\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[45]{m}},
portion = {\portion{5-7}},
source = Emeril
]
{Penne a La Vodka Casserole}

\ingredients{
4 tablespoons extra virgin olive oil\\ 
1 pound sweet Italian sausage\\ 
%, cut crosswise into 1 inch slices
1 pound hot Italian sausage\\
%, cut crosswise into 1 inch slices
4 cups thinly sliced onions\\ 
1 $\frac{3}{4}$ = teaspoons salt\\ 
$\frac{3}{4}$ teaspoon freshly ground black pepper\\ 
$\frac{1}{4}$ cup thinly sliced fresh basil leaves\\ 
1 tablespoon minced garlic\\ 
$\frac{1}{2}$ cup vodka\\ 
2 (16 ounce) cans crushed tomatoes w/ juice\\ 
1 teaspoon essence\\ 
$\frac{1}{2}$ cup heavy cream\\ 
1 tablespoon olive oil\\ 
1 pound penne pasta\\ 
15 ounces ricotta\\ 
1 cup grated parmigaino-reggiano\\ 
1 $\frac{1}{2}$ cups grated mozzarella\\ 
}

\preparation{
\step Preheat oven to 350 degrees. Then cut sausages crosswise into 1 inch slices.
\step Heat 2 tablespoons extra virgin olive oil in large skillet over high heat. Add the sausage and cook stirring until browned, 4 to 5 minutes.
\step Add the onions, $\frac{3}{4}$ teaspoon salt and the black pepper.
\step Cook, stirring occasionally until the onions are just soft about 4 minutes.
\step Add the basil and garlic and cook, stirring for 2 minutes. Then Add the vodka and tomatoes, reduce the heat to medium-low and simmer, uncovered stirring occasionally for 40 minutes.
\step Add the essence and heavy cream, stir to mix and simmer for 5 minutes. Then, remove from the heat.
\step To cook the pasta, combine 4 quarts water, the 1 tablespoon olive oil and the remaining 1 teaspoon of salt in the large pot over high heat. Bring to the boil, add the pasta and cook 14-15 minutes.
\step Remove from the heat and drain well. Combine half of the ricotta cheese and half of the Parmigiano-Reggiano with the remaining 2 tablespoons extra-virgin olive oil in a large mixing bowl.
\step Add the pasta and toss to coat evenly. Add the sausage mixture and mix well. Add the remaining Parmigiano-Reggiano and mix well.
\step Transfer the mixture to a 9 by 13 inch baking dish. Sprinkle with the mozzarella and bake until bubbly and golden about 45 minutes.
\step Remove from the oven. Serve warm.
}
\end{recipe}
