\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[45]{m}},
portion = {\portion{5-7}},
source = Giada De Laurentis
]
{Penne with Shrimp and Herbed Cream Sauce}

\ingredients{
1 pound penne pasta\\ 
$\frac{1}{4}$ cup olive oil\\ 
1 pound medium shrimp, peeled/deveined\\ 
4 cloves garlic, minced\\ 
$\frac{1}{2}$ teaspoon kosher salt\\ 
$\frac{1}{2}$ teaspoon freshly ground black pepper\\ 
1 (15 ounce can) chopped tomatoes\\ 
%  (Delmonte olive oil, garlic \& basil)
$\frac{1}{2}$ cup chopped fresh basil leaves\\ 
$\frac{1}{2}$ cup chopped fresh flat leaf parsley\\ 
$\frac{1}{4}$ teaspoon crushed red pepper flakes\\ 
1 cup white wine\\ 
1/3 cup clam juice\\ 
$\frac{3}{4}$ cup whipping cream\\ 
$\frac{1}{2}$ cup grated Parmesan\\ 
}

\preparation{
\step Bring to a large pot of salted water to a boil over high heat. Add the pasta and cook until tender. Then drain the pasta and set aside.
\step In a large skillet, heat the oil over medium high heat. Add the shrimp, garlic, $\frac{1}{2}$ teaspoon of salt, and $\frac{1}{2}$ teaspoon of pepper. 
\step Cook, stirring frequently until the shrimp turn pink and are cooked through, about 3 minutes. 
\step Using a slotted spoon, remove the shrimp from the pan and set aside.
\step Add the tomatoes, $\frac{1}{4}$ cup basil, $\frac{1}{4}$ cup parsley and the red pepper flakes. Cook for 2 minutes, stirring constantly.
\step Add the wine, clam juice, and heavy cream. Bring the mixture to a boil.
\step Reduce the heat to medium-low and simmer for 7 to 8 minutes until the sauce thickens.
\step Add $\frac{1}{4}$ cup of the Parmesan, the cooked shrimp, the cooked pasta and the remaining herbs. Toss together until all ingredients are coated. 
\step Season to taste with extra salt and pepper. Then, transfer the pasta to a large serving bowl. Sprinkle with the remaining cheese and serve.
}
\end{recipe}
