\newrecipe
\begin{recipe}
[
preparationtime = {\unit[40]{m}},
portion = {\portion{4-5}},
source = Steve
]
{Spaghetti and Meatballs}

\ingredients{
1 pound spaghetti\\ 
sprinkle of salt\\ 
\textbf{For the Meatballs:}\hspace*{\hfill}\\ 
1 pound ground Italian sausage\\ 
$\frac{1}{2}$ chopped white onion\\ 
2 teaspoons Worcestershire sauce\\ 
1 egg, beaten\\ 
$\frac{1}{2}$ cup Italian bread crumbs\\ 
$\frac{1}{4}$ cup grated Parmesan\\ 
%, Parmigiano-Reggiano or Romano cheese
2 cloves garlic, chopped\\ 
Salt and pepper\\ 
\textbf{For the sauce:}\hspace*{\hfill}\\ 
2 tablespoons extra-virgin olive oil\\ 
$\frac{1}{2}$ teaspoon paprika\\ 
4 cloves garlic, crushed or chopped\\ 
1 small onion, finely chopped\\ 
$\frac{1}{2}$ cup beef stock\\ 
$\frac{1}{2}$ cup red wine\\ 
1 (28-ounce) can crushed tomatoes\\ 
A handful chopped flat-leaf parsley\\ 
10 leaves fresh basil leaves\\ 
%, torn or thinly sliced
}

\hint{For a smoother sauce, you can pulse blend the sauce ingredients before cooking.}

\preparation{
\step Place a large pot of water (sprinkled with salt) to boil. When it boils, add pasta and cook to al dente.
\step In a bowl, mix sausage, Worcestershire, egg, white onion, bread crumbs, cheese, garlic, salt and pepper.
\step Hand roll meat into 1 1/2 inch medium-sized meatballs.
\step Heat a small amount of oil in a large sauce pan up to medium-high. Then add the meatballs and, turning them to brown all sides.
\step Make the sauce on the meatballs by adding oil, crushed pepper, garlic and finely chopped onion. Saute 5 to 7 minutes, until onion bits are soft.
\step Add the beef stock, wine, crushed tomatoes, and herbs. Bring to a simmer and cook on low covered for about 20 minutes.
\step Drain pasta and serve hot with a ladle of the sauce with some meatballs and grated cheese. 
}
\end{recipe}
