\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1.25]{h}},
bakingtime = {\unit[45]{m}},
portion = {\portion{8-12}},
source = Emeril Lagasse
]
{Double Cut Pork Chops with Caramelized Onion Gravy and Pecan Glazed Sweet Potatoes}

\ingredients{
\textbf{Caramelized onion gravy:}\hspace*{\hfill}\\ 
2 tablespoons butter\\ 
3 cups thinly sliced onions\\ 
1 tablespoon light brown sugar\\ 
1 teaspoon garlic\\ 
1 teaspoon thyme leaves\\ 
2 tablespoons all-purpose flour\\ 
1 cup chicken stock\\ 
Salt \& pepper\\ 
\\ 
\textbf{Pecan Glazed Sweet Potatoes:}\hspace*{\hfill}\\ 
1 $\frac{1}{2}$ pounds sweet potatoes\\ 
1 tablespoon olive oil\\ 
Salt and pepper\\ 
6 tablespoons butter\\ 
$\frac{1}{2}$ cup light brown sugar\\ 
$\frac{1}{2}$ cup pecans\\ 
\\ 
\textbf{Pork chops:}\hspace*{\hfill}\\ 
4 double cut bone in pork chops\\ 
1 tablespoon essence\\ 
2 teaspoons salt\\ 
2 tablespoons olive oil.\\ 
}

\preparation{
\\ \textbf{Gravy:}
\step In a small saucepan set over medium heat, add the butter.
\step Once melted, add the onions and sugar to the pan and sweat, stirring occasionally until wilted and well caramelized, about 18 to 20 minutes.
\step Add the garlic and thyme to the pan and saut\'{e} until fragrant, about 30 seconds.
\step Add the flour to the pan and stir to make a roux, about 2 to 3 minutes.
\step Add the chicken stock. Bring to a boil and reduce heat to a simmer for 15 minutes and season with the salt and pepper.\\ 
\\ \textbf{Sweet potatoes:}
\step Wash the sweet potatoes and peel. Chop the sweet potatoes into 1 inch pieces and place in a roasting pan. Drizzle with the olive oil and season with the salt and pepper.
\step Place the potatoes in the oven and roast until tender about 30 minutes. Remove from the oven and set aside.
\step In a large 12 inch saut\'{e} pan, add the butter and brown sugar.
\step When the butter begins to boil with the sugar, add the pecans and the sweet potatoes. 
\step Continue to cook, tossing occasionally, until the potatoes are well glazed, about 3 minutes.\\ 
\\ \textbf{Pork chops:}
\step Preheat the oven to 400 degrees. Set a large 12inch saut\'{e} pan over medium-high heat.
\step Add the olive oil to the pan and once hot, place the pork chops in the pan. Sear the pork chops until well caramelized about 5 minutes.
\step Turn over and sear on the second side for an additional 5 minutes.\\ 
\step Remove the pan from the stove top and place in the oven. Roast the pork chops until a thermometer reaches 150 degrees about 10 to 12 minutes for medium.
\step Remove the chops from the oven and serve with the glazed sweet potatoes and the caramelized onion gravy.
\step Garnish with chopped parsley.
}
\end{recipe}
