\newrecipe
\begin{recipe}
[
preparationtime = {\unit[2]{h}},
bakingtime = {\unit[30]{m}},
portion = {\portion{4}},
sorurce = Smitten Kitchen
]
{Pancetta, White bean, and Chard Pot Pie}

\ingredients{
\textbf{For the lid:}\hspace*{\hfill}\\ 
2 cups all-purpose flour\\ 
1/2 teaspoon table salt\\ 
13 tablespoons cold unsalted butter\\ 
%, diced
6 tablespoons (90 grams) sour cream\\ 
%or whole Greek yogurt\\ 
1 tablespoon (15 ml) white wine vinegar\\ 
1/4 cup (60 ml) ice water\\ 
1 egg\\ 
1 tablespoon water\\ 
% Beat top two together for egg wash
\textbf{For the filling:}\hspace*{\hfill}\\ 
2 tablespoons (30 ml) olive oil\\ 
4 ounces 1/4-inch-diced pancetta\\ 
1 large or 2 small onions, finely chopped\\ 
1 large carrot, finely chopped\\ 
1 large stalk celery, finely chopped\\ 
Pinch of red pepper flakes\\ 
Salt and freshly ground black pepper\\ 
2 garlic cloves, minced\\ 
8-10 ounce Swiss chard \\ 
%Thinly sliced Swiss chard leaves from an (225- to 285-gram)
%bundle (4 cups); if leaves are very wide, you can halve them lengthwise
3 1/2 tablespoons butter\\ 
3 1/2 tablespoons all-purpose flour\\ 
3 1/2 cups chicken broth\\ 
2 cups cooked and drained white beans\\ 
%cooked and drained, or from one and a third 15.5- ounce (440-gram) cans
}

\hint{You can prepare most of this in advance and place in the fridge to ease cooking time.}

\preparation{
\\ \\ \textbf{Make lids:}
\step In a large, wide bowl, combine the flour and salt. Add the butter and, using a pastry blender, cut them up and into the flour mixture until it resembles little pebbles. 
\step Keep breaking up the bits of butter until the texture is like uncooked couscous.
\step In a small dish, whisk together the sour cream, vinegar, and water, and combine it with the butter-flour mixture.
\step Using a flexible spatula, stir the wet and the dry together until a craggy dough forms. If needed, get your hands into the bowl to knead it a few times into one big ball. 
\step Pat it into a flattish ball, wrap it in plastic wrap, and chill it in the fridge for 1 hour or up to 2 days (it will last a couple months in the freezer).

\\ \textbf{Make filling:}
\step Heat 1 tablespoon olive oil over medium-high heat in a large, wide saucepan, and then add the pancetta.
\step Brown the pancetta, turning it frequently, so that it colors and crisps on all sides; this takes about 10 minutes. Remove it with a slotted spoon, and drain it on paper towels before transferring to a medium bowl.
\step Leave the heat on and the renderings in the pan. Then add an additional tablespoon of olive oil if needed and heat it until it is shimmering.
\step Add onions, carrot, celery, red pepper flakes, and a few pinches of salt, and cook over medium heat until the vegetables are softened and begin to take on color, about 7 to 8 minutes.
\step Add the garlic, and cook for 1 minute more.\\ 
\step Thinly slice the chard, add, and cook until wilted, about 2 to 3 minutes. Season with the additional salt and freshly ground black pepper to taste.
\step Transfer all of the cooked vegetables to the bowl with the pancetta, and set aside.\\ 

\\ \textbf{Make sauce:}
\step Wipe out the large saucepan; don’t worry if any bits remain stuck to the bottom. Then melt the butter in the saucepan over medium-low heat.
\step Add the flour, and stir with a whisk until combined. Continue cooking for 2 minutes, stirring the whole time, until it begins to take on a little color.
\step Whisk in the broth, one ladleful at a time, mixing completely between additions. Once you’ve added one- third of the broth, you can begin to add the rest more quickly, two to three ladlefuls at a time.

\step Once all of the broth is added, stirring the whole time, bring the mixture to a boil and reduce it to a simmer.
\step Cook the sauce until it is thickened and gravylike, about 10 minutes. Season with salt and pepper.
\step Stir the white beans and reserved vegetables into the sauce.\\ 

\\ \textbf{Assemble and cook pot pies:}\\ 
\step Preheat your oven to 375 degrees. Divide the filling between four ovenproof 2-cup bowls. (You’ll have about 1 1/2 cups filling in each.)
\step Set the bowls on a baking pan. Divide the dough into four pieces, and roll it out into rounds that will cover your bowls with an overhang, or about 1 inch wider in diameter than your bowls. 
\step Whisk the egg and tablespoon of water to make an egg wash and brush it lightly around the top rim of your bowls and drape the pastry over each, pressing gently to adhere it. 
\step Brush the lids with egg wash, then cut small, decorative vents in each to help steam escape. 
\step Bake until crust is lightly bronzed and filling is bubbling, about 30 to 35 minutes.
}
\end{recipe}
