\begin{recipe}
[
preparationtime = {\unit[1]{h}},
portion = {\portion{4-6}},
]
{Pork Chops, Cabbage and Apples}

% or 1 teaspoon dried thyme
%  or 1 teaspoon dried sage
\ingredients{
3 teaspoons paprika\\
2 teaspoons fresh chopped thyme\\ 
2 teaspoons kosher salt\\ 
1 $\frac{1}{2}$ teaspoon fresh chopped sage\\ 
6 (1/2 inch thick) pork loin chops\\ 
2 bacon slices\\ 
1 head cabbage coarsely chopped\\ 
2 medium onions, thinly sliced\\ 
1 large Granny Smith apple\\ 
1 tablespoon tomato paste\\ 
1 (12 ounce) bottle lager beer\\ 
}

\preparation{
\step Wash, peel, and slice the apple.\\
\step Combine 2 teaspoons paprika, 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried thyme, 1 teaspoon salt, 1 teaspoon pepper and 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried sage, rub evenly overly pork chops.
\step Cook bacon slices in large, deep skillet over medium high heat 6 to 8 minutes or until crisp; remove bacon and drain on paper towels, reserving drippings in skillet.
\step Crumble bacon up when cool enough.\\ 
\step Cook pork in hot drippings 3 minutes on each side or until browned and done; remove pork from pan and keep warm.
\step Add cabbage, onions and apple to pan. Cover and reduce heat to medium; cook stirring occasionally 15 minutes or until cabbage begins to wilt.
\step Add tomato paste, beer, the crumbled bacon, 1 teaspoon paprika, 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried thyme, 1 teaspoon salt, $\frac{1}{2}$ teaspoon pepper and 1 teaspoon fresh or $\frac{1}{2}$ teaspoon dried sage, stirring to loosen particles from bottom of skillet.
\step Cover and cook 15 minutes or until cabbage is tender and liquid is slightly thickened.\\ 
\step Add pork, and cook uncovered 5 minutes or until thoroughly heated.
}

\hint{
Instead of the fresh thyme, you can use 1 teaspoon dried thyme and instead of fresh sage, you can use 1 teaspoon dried sage.}

\end{recipe}
