\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
portion = {\portion{20}},
source = Emeril Lagasse
]
{Pork Egg Rolls with Sweet and Sour Sauce}

\ingredients{
2 tablespoons vegetable oil\\ 
1 pound ground pork\\ 
$\frac{1}{2}$ cup minced onion\\ 
1 tablespoon chopped garlic\\ 
1 pound bok choy, shredded\\ 
$\frac{1}{2}$ pound medium shrimp\\ 
1 tablespoon dark sesame oil\\ 
Soy sauce to taste\\ 
$\frac{1}{4}$ cup sake (optional)\\ 
1 tablespoon sugar\\ 
1 pound fresh bean sprouts\\ 
$\frac{1}{4}$ cup green onions, green part only\\ 
20 (6 inch) egg roll wrappers\\ 
1 egg beaten for egg wash\\ 
Oil for frying\\ 
}

\preparation{
\step  Preheat the fryer. If not done already, peel, devein and chop shrimp and wash and pat down bean sprouts.
\step In a wok, heat the oil. When the oil is hot, add the pork. Season with salt and pepper. Stir fry for 3 minutes.
\step Add the onions and garlic, continue to cook for 2 minutes.
\step Add the bok choy and shrimp. and season with salt and pepper. Stir-fry for 1 minute. Season with the sesame oil, soy sauce, sake and sugar.
\step Add the sprouts and green onions and mix thoroughly. Remove from the heat and cool completely.
\step To assemble, spoon about $\frac{1}{4}$ cup of the filling in a rectangular shape on the center of each wrapper. Then, fold in the ends toward the center about $\frac{1}{4}$ inch. 
\step Beginning at the bottom roll up the wrapper, like a jelly roll, using a little of the egg wash to seal the end tightly.
\step Repeat until all of the egg rolls are done.\\ 
\step Fry the egg rolls in batches until golden brown stirring occasionally for overall browning, about 2 to 3 minutes.s
\step Remove from the oil and drain on paper towels. Season with essence.\\ 
\step Serve warm with sweet and sour sauce.
}
\end{recipe}
