\newrecipe
\begin{recipe}
[
preparationtime = {\unit[45]{m}},
bakingtime = {\unit[1.5]{h}},
portion = {\portion{10-12}},
]
{Sugarcane Baked Ham with Spiced Apples and Pears}

\hint{The ham should be about 8-10 pounds and spiral sliced}

\ingredients{
12 sugarcane swizzle sticks\\
%, each cut into about 3 inch pieces
1 hickory smoked ham (no bone, cooked)\\ 
% 8-10 pounds spiral slice ham
1 $\frac{1}{2}$ pound ($\sim$4) Granny Smith apples\\ 
1 $\frac{1}{2}$ pound ($\sim$4) Bartlett pears\\ 
\\ \textbf{Glaze:}\hspace*{\hfill}\\ 
1 cup firmly packed light brown sugar\\ 
1 cup Steens 100\% Pure Cane Syrup\\ 
$\frac{1}{2}$ cup dark molasses\\ 
$\frac{1}{2}$ cup dark corn syrup\\ 
1/8 teaspoon freshly grated nutmeg\\ 
$\frac{1}{4}$ teaspoon ground cloves\\ 
1/8 teaspoon ground allspice\\ 
$\frac{1}{2}$ teaspoon ground cinnamon\\ 
1 teaspoon dried mustard\\ 
$\frac{1}{4}$ cup water\\ 
}

\preparation{
\step Preheat oven to 350 degrees. Line a shallow baking pan with parchment or waxed paper.
\step Cut the sugarcane sticks each into about 3 pieces then insert the sugarcane sticks into the ham at 3 to 4 inch intervals. 
\step Tie the ham, using kitchen twine, horizontally and vertically, like a package to hold it together. Place it on a wire rack in the baking pan.
\step In a mixing bowl, combine all the glaze ingredients together except for the mustard and water; mix well. 
\step In a small bowl, dissolve the mustard in the water, then add to the spice mixture; blend well.
\step Brush the entire ham with the glaze, coating it evenly.
\step Wash, core and halve the fruit. Place all around the ham.
\step Baste the ham a second time and baste the fruit with the glaze.
\step  Bake for 45 minutes. Then baste the ham and fruit again. Bake another 45 minutes. Then remove the ham from the oven and let is rest for 5 minutes.
\step Remove and discard the string and swizzle sticks. Then serve the apples and pears on a platter with the ham.
}
\end{recipe}
