\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[40]{m}},
portion = {\portion{4-6}}
]
{Apple-Oatmeal Crisp with Irish Whiskey Cream}

\ingredients{
1 stick cold unsalted butter (in pieces)\\ 
2 pounds Rome apples\\ 
2 tablespoons fresh lemon juice\\ 
1 cup packed light brown sugar\\ 
1 cup all purpose flour\\ 
2 tablespoons Irish Whiskey\\ 
1 teaspoons cinnamon\\ 
$\frac{1}{4}$ teaspoon cardamom\\ 
Pinch salt\\ 
$\frac{1}{4}$ cup Irish oatmeal\\ 
$\frac{1}{4}$ cup toasted, chipped walnut pieces\\ 
\\ 
\textbf{Irish Whiskey Cream:}\hspace*{\fill}\\ 
1 cup heavy cream\\ 
1 tablespoon sugar\\ 
2 tablespoons Irish whiskey\\ 
}

\preparation{
\step Peal, core, and slice the apples.\\ 
\step Preheat the oven to 375 degrees. Lightly butter an 11 by 7 inch baking pan and set aside.
\step In a large skillet, melt 3 tablespoons of butter over medium-high heat.
\step Add the apples, lemon juice, $\frac{1}{2}$ cup of the brown sugar and 1 tablespoon of the flour to the butter. Stir well and cook for 5 minutes.
\step Add the whiskey, cinnamon, cardamom and salt to the mixture, stir well and cook for 1 minute. Remove from the heat.
\step In a large bowl combine the remaining flour, oatmeal and remaining $\frac{1}{2}$ cup sugar.
\step Add the remaining 5 tablespoons of butter and mix well.
\step Put mixture in pan and bake about 35 to 40 minutes until crisp is golden.
\step Whip the cream until it begins to form soft peaks. Then, add the sugar and whiskey and beat until stiff peaks form.
\step Cover and chill the cream then seat hot with the Irish Whiskey cream.
}
\end{recipe}