\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[45]{m}},
portion = {\portion{3-5}},
source = Tyler Florence
]
{Bourbon Peach Cobbler}

\ingredients{
8 peaches\\ 
$\frac{1}{4}$ cup bourbon\\ 
$\frac{3}{4}$ cup sugar, plus more for dusting\\ 
2 tablespoons corn starch\\ 
1 teaspoon ground cinnamon\\ 
1-1/2 cups all purpose flour\\ 
2 teaspoons baking powder\\ 
$\frac{1}{2}$ teaspoon kosher salt\\ 
16 tablespoons (2 sticks) cold unsalted butter\\ 
$\frac{3}{4}$ cup heavy cream, plus more for brushing\\ 
}

\preparation{
\step Heat the oven to 375 degrees. Then, peel and slice the peaches to make 6-8 cups.\\ 
\step In a large bowl add the peaches, bourbon, $\frac{1}{4}$ cup sugar, cornstarch and cinnamon and mix well to coat the peaches evenly; set aside.
\step Prepare the dumplings: Into a bowl sift together the flour, $\frac{1}{2}$ cup sugar, baking powder and salt.
\step Cut 12 tablespoons (1-1/2 sticks) butter into small pieces. Add it to the flour mixture and cut it in with a pastry blender or your hands until the mixture looks like coarse bread crumbs. \step Pour in the cream and mix just until the dough comes together. Don't overwork the dough; it should be slightly sticky but manageable.
\step In a 10 inch cast iron skillet over medium low heat, melt the remaining 4 tablespoons butter. 
\step Add the peaches and cook gently until heated through about 5 minutes.\\ 
\step Drop the dough by  tablespoonfuls over the warm peaches. There can be gaps, the dough will puff up and spread out as it bakes.
\step Brush the top with some heavy cream and sprinkle with some sugar; put it into the oven on a baking sheet to catch any drips. 
\step Cook for 40 to 45 minutes until the top is browned and the fruit is bubbling.
}
\end{recipe}