\newrecipe
\begin{recipe}
[
preparationtime = {\unit[40]{m}},
bakingtime = {\unit[30]{m}},
portion = {\portion{4-5}}
]
{Chocolate Chip Pie}

\ingredients{
\textbf{Pie:}\hspace*{\fill}\\ 
2 $\frac{3}{4}$ cups all purpose flour\\ 
1 $\frac{1}{2}$ teaspoons salt\\ 
1 teaspoon baking soda\\ 
1 $\frac{1}{4}$ teaspoons baking powder\\ 
1 cup (2 sticks) unsalted butter, softened\\ 
1 $\frac{1}{2}$ cups packed brown sugar\\ 
$\frac{1}{2}$ cup granulated sugar\\ 
3 large eggs\\ 
1 tablespoon vanilla extract\\ 
3 cups semisweet chocolate chips\\ 
2 cups chopped walnuts, optional\\ 
\textbf{Whipped cream:}\hspace*{\fill}\\ 
2 pints (4 cups) heavy cream\\ 
$\frac{1}{4}$ cup confectioners sugar\\ 
$\frac{1}{4}$ cup miniature semisweet chocolate chips\\ 
}

\preparation{
\step Preheat oven to 350 degrees. Grease 2 (9 inch) pie plates; set aside.
\step In a large bowl, sift together the flour, salt, baking soda and baking powder.
\step In the bowl of an electric mixer, cream together butter, brown sugar and granulated sugar.
\step Add the eggs, 1 at a time, beating until incorporated. Then beat in the vanilla.
\step Add flour mixture a little at a time and mix until fully combined.
\step Fold in the 3 cups chocolate chips and if desired the walnuts.
\step Divide the dough between the prepared pie plates and smooth the tops with a spatula.
\step Bake about 30 minutes or until pies are golden and slightly firm to the touch but still soft.
\step If the pies begin to darken too much before they are based through, over with foil and continue baking.
\step Let pies cool completely on a wire rack. While the pies cool, whip the cream and confectioners sugar until soft peaks form (tips curl).
\step Fold in the chocolate chips.\\ 
\step Refrigerate whipped cream until ready to use.\\ 
\step Spread the whipped cream over the pies and serve.\\ 
}
\end{recipe}