\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{m}},
bakingtime = {\unit[15]{m}},
portion = {\portion{5-8}},
]
{Chocolate Marshmallow Pie}

\ingredients{
\textbf{For the crust:}\hspace*{\hfill}\\ 
12 whole chocolate graham crackers\\ 
%, roughly broken
3 tablespoons granulated sugar\\ 
1 stick unsalted butter, melted\\ 
\textbf{For the filling:}\hspace*{\hfill}\\ 
1 stick unsalted butter\\ 
8 oz. milk chocolate, chopped\\ 
$\frac{1}{2}$ cup granulated sugar\\ 
2 large eggs\\ 
2 tsp. Vanilla extract\\ 
$\frac{1}{2}$ tsp. salt\\ 
$\frac{1}{2}$ cup flour\\ 
\textbf{For the topping:}\hspace*{\hfill}\\ 
1 cup cold heavy cream\\ 
$\frac{2}{3}$ cup marshmallow cream\\ 
1 tbsp. confectioners sugar\\ 
Shaved chocolate for topping\\ 
}

\preparation{
\step Preheat the oven to 350 degrees. Roughly break up the graham crackers.\\ 
\\ \textbf{Make the crust:}
\step Pulse the graham crackers and granulated sugar in a food processor until finely ground.
\step Add the melted butter and pulse a few times until combined. Press the mixture into the bottom and up the side of a 9 inch pie plate, making a thicker rim around the edge.
\step Bake until the top edge is firm and the bottom is dry about 15 minutes. Transfer to a rack and let cool completely.\\ 
\\ \textbf{Make the filling:}
\step Melt the butter and chocolate in a medium saucepan over medium heat, stirring occasionally until smooth.
\step Transfer to a medium bowl and let mixture cool 5 minutes.
\step Whisk in the granulated sugar, eggs, vanilla and salt until smooth.\\ 
\step Whisk in the flour until combined. Then, pour the filling into the cooled crust.\\ 
\step Bake until the filling is set and a toothpick inserted into the center comes out clean, 35 to 40 minutes.
\step Transfer to a rack and let cool completely.\\ 
\\ \\ \textbf{Make the topping.}
\step Combine the heavy cream, marshmallow cream and confectioners sugar in a food processor and pulse, scraping down the processor until the mixture is thick.
\step Spoon the topping onto the center of the pie. Top with shaved chocolate.
}
\end{recipe}