\newrecipe
\begin{recipe}[
preparationtime = {\unit[4.5]{h}},
portion = {\portion{5-7}},
source = Mom's recipe
]
{Christmas Trifle}

\ingredients{
1 pound cake (any flavor)\\ 
\textbf{Filling:}\hspace*{\fill}\\ 
1 quart milk\\ 
2 cups sugar\\ 
1 teaspoon vanilla\\ 
10 large egg yolks, beaten\\ 
$\frac{1}{2}$ cup cornstarch (dissolved in water)\\ 
$\frac{1}{2}$ cup water\\ 
2 tablespoons unsalted butter\\ 
\textbf{To assemble the trifle:}\hspace*{\fill}\\ 
1 quart heavy cream\\ 
$\frac{1}{4}$ cup sugar\\ 
1 cup orange flavored liqueur (Grand Marnier)\\ 
4-6 pints fresh raspberries\\ 
}

\preparation{
\\ \textbf{Filling:} 
\step Combine the milk, sugar and vanilla in a large heavy bottomed saucepan over medium-high heat. Whisk to dissolve the sugar.
\step When the mixture comes to a simmer after 5 minutes, take 1 cup of the milk and sugar mixture and add it to the yolks. Whisk to blend well.
\step Slowly add the yolks to the milk and sugar mixture in the saucepan, whisking constantly. \step Cook over medium heat until it thickens slightly, 4 to 5 minutes, whisking occasionally.
\step Over medium heat, slowly add this mixture to the saucepan, whisking constantly for 1 minute. Using a wooden spoon, continue stirring for about 2 minutes.
\step Add the butter and stir until it is completely melted and the mixture has thickened to a custard, about 2 minutes.
\step Pour the mixture into a glass bowl. Cover with plastic wrap, pressing the wrap down on the surface of the custard to prevent a skin from forming.
\step Cool completely and chill for at least 4 hours.\\ \\ 
\\ \textbf{To assemble the trifle:}
\step Cut the cake into 1 inch cubed size pieces.\\ 
\step Beat the cream with an electric mixer on high speed for about 2 minutes.\\ 
\step Add the sugar and beat until a mixture is thick and forms soft peaks, 1 to 2 minutes. Set aside.
\step Beat the custard with a wire whisk until it is smooth. Set aside.\\ 
\step Spread out the cubed pound cake evenly on a piece of parchment paper. Drizzle the orange liqueur over the pound cake.
\step Spread 1 cup of the cream filling on the bottom of a large, deep glass trifle bowl. Top with a layer of pound cake.
\step Arrange raspberries on top of the pound cake. Then, spread 2 cups of the cream on top of the raspberries. Top with more pound cake, then raspberries.
\step Spread another cup of the cream and top with the remaining pound cake and raspberries. Then, spread the remaining cream on top of the raspberries.
\step Mound the whipped cream evening over the top.\\ 
\step Serve immediately or keep chilled until ready to serve.
}
\end{recipe}
