\newrecipe
\begin{recipe}[
preparationtime = {\unit[30]{m}},
bakingtime = {\unit[55]{m}},
portion = {\portion{3-5}},
source = Emeril
]
{Honey Spice Cake with Rum Glaze}

\ingredients{
2 and 1/3 cups sifted cake flour\\ 
1 $\frac{1}{2}$ teaspoons baking powder\\ 
$\frac{1}{2}$ teaspoon baking soda\\ 
1 teaspoon ground ginger\\ 
1 teaspoon ground cinnamon\\ 
$\frac{1}{2}$ teaspoon ground cloves\\ 
$\frac{1}{2}$ teaspoon salt\\ 
1 $\frac{1}{2}$ sticks unsalted butter\\ 
2/3 cup real honey\\ 
$\frac{1}{2}$ cup sugar\\ 
3 large egg yolks\\ 
$\frac{3}{4}$ cup plus 2 tablespoons plain yogurt\\ 
4 large egg whites\\ 
1 $\frac{1}{4}$ cups sifted powdered sugar\\ 
1 $\frac{1}{2}$ teaspoons rum\\ 
}

\preparation{
\step Preheat oven to 350 degrees. Grease and flour 1 tube or bundt pan.
\step Sift the cake flour, baking power, baking soda, ginger, cinnamon, cloves and salt together, then sift again into a large bowl.
\step In another large bowl, beat the butter with an electric mixer on high speed until creamy.
\step Gradually add the honey and $\frac{1}{4}$ cup of the sugar to the butter and beat on high speed until well mixed, 2 to 4 minutes.
\step Beat in the egg yolks, 1 at a time. Beat on low and add the flour mixture in 3 parts, alternating with the yogurt in 2 parts.
\step Beat until smooth, scraping down the side of the bowl as necessary.
\step In another large bowl, beat the egg whites until soft peaks form.
\step Gradually add the remaining $\frac{1}{4}$ cup sugar, beating on high speed, until stiff.\\ 
\step Fold the egg whites into the batter. Then, pour the batter into the prepared pan and bake until a tester comes up clean 40 to 55 minutes.
\step Let the cake cool in the pan on a wire rack for 10 minutes and then invert the cake onto the rack and allow to cool completely.
\step In a small bowl combine the powdered sugar and sum and still to combine. Mixture should be a stiff glaze. If the glaze is too thick, thin with a bit of milk.
\step Using a spoon, drizzle the glaze all over the cake in a radom pattern. Let the cake sit until the glaze has hardened. Then serve.
}
\end{recipe}
