\newrecipe
\begin{recipe}
[
preparationtime = {\unit[1]{h}},
bakingtime = {\unit[1.25]{h}},
portion = {\portion{4-5}},
sourece = Emeril w/ Mom's changes
]
{Pumpkin Cheesecake with Bourbon Spiked Cream}

\ingredients{
\\ \textbf{Cake:}\hspace*{\hfill}\\ 
1 $\frac{1}{2}$ cups ginger snaps crushed into crumbs\\ 
1 cup ground pecan pieces\\ 
1 stick melted butter\\ 
2 lbs cream cheese, softened and cubed\\ 
1 cup light brown sugar\\ 
6 eggs\\ 
$\frac{1}{2}$ cup heavy cream\\ 
$\frac{1}{2}$ cup all purpose flour\\ 
Pinch salt\\ 
$\frac{1}{2}$ teaspoon cinnamon\\ 
1 teaspoon vanilla\\ 
2 cups pumpkin puree\\ 
2 cups sweetened whipped cream\\ 
Dash bourbon\\ 
1 cup warm semisweet chocolate sauce\\ 
\textbf{Chocolate sauce:}\hspace*{\hfill}\\ 
$\frac{3}{4}$ cup half \& half\\ 
1 tablespoon butter\\ 
$\frac{1}{2}$ pound semisweet chocolate chips\\ 
$\frac{1}{4}$ teaspoon vanilla\\ 
}

\preparation{\\ 
\\ \textbf{Cake:}
\step Preheat oven to 350 degrees.\\ 
\step Combine the crumb, ground pecans and butter together. Mix well and press into a 12 inch spring form pan.
\step In a food processor (or mixer) with the metal blade, mix the cream cheese until smooth.
\step Add the brown sugar and blend.\\ 
\step Add the eggs 1 at a time to thoroughly incorporate into the cheese mixture.
\step Add the heavy cream. Add the flour, salt, cinnamon and vanilla and blend until smooth.
\step Add the mashed pumpkin and blend until smooth.\\ 
\step Pour into the prepared pan. Bake 1 hour and 15 minutes or until the cake is set.
\step Remove from the oven and with a knife loosen the sides from the pan. This will prevent the cake from splitting down the center.
\step Completely cool the cake before cutting.\\ 
\step Combine the whipped cream and bourbon together, blend well. Garnish each piece of cake with the Bourbon Whipped cream and a drizzle of chocolate sauce.
\\ 
\\ \textbf{Chocolate sauce:}
\step Combine the half and half and butter in a small heavy bottomed saucepan over medium heat. 
\step Heat the mixture until a thin paper like skin appears on the top. Do not boil.\\ 
\step Add the chocolate and vanilla and stir until the chocolate melts and the mixture is smooth.
\step Remove from the heat and let cool.
}
\end{recipe}
