\newrecipe
\begin{recipe}
[
preparationtime = {\unit[40]{m}},
bakingtime = {\unit[20]{m}},
portion = {\portion{3-4}},
source = Emeril
]
{Raspberry Lemon Thumbprint Cookies}

\ingredients{
$\frac{1}{2}$ cup raspberry jam\\ 
1 tablespoon Chambord\\ 
2 $\frac{1}{4}$ cups all purpose flour\\ 
1 teaspoon baking powder\\ 
$\frac{1}{4}$ teaspoon salt\\ 
2 sticks butter at room temperature\\ 
2/3 cup sugar\\ 
2 large egg yolks\\ 
1 tablespoon finely grated lemon zest\\ 
1 tablespoon fresh lemon juice\\ 
1 teaspoon pure vanilla extract\\ 
}

\preparation{
\step Preheat oven to 350 degrees. Lightly butter 2 large baking sheets
\step In a small bowl combine the jam and Chambord. Stir to combine.
\step In a medium bowl, combine the flour, baking powder and salt and whisk to blend.
\step In a large bowl using an electric mixer, beat the butter and sugar until light and creamy.
\step Beat in the egg yolks, lemon zest, lemon juice and vanilla.
\step Add the flour mixture in 2 additions and beat just until moist clumps form.
\step Gather the dough together into a ball.\\ 
\step Pinch off the dough to form 1 inch balls. Place on the prepared baking sheets, spacing 1 inch apart.
\step Use your floured index finger or $\frac{1}{2}$ teaspoon measuring spoon to create depressions in the center of each ball.
\step Fill each indentation with nearly $\frac{1}{2}$ teaspoon of the jam mixture.\\ 
\step Bake until golden brown (about 20 minutes).\\ 
\step Transfer the cookies to wire racks and cool completely.
}
\end{recipe}
