\newrecipe
\begin{recipe}
[
preparationtime = {\unit[2.5]{h}},
bakingtime = {\unit[25]{m}},
portion = {\portion{5-6}}
]
{Swedish Tea Ring}

\ingredients{
2 cups milk\\ 
1 package yeast\\ 
$\frac{1}{4}$ cup water\\ 
2 tablespoons butter\\ 
2 tablespoons sugar\\ 
6 cups sifted flour\\ 
1 tablespoon melted butter\\ 
3 tablespoons butter\\ 
3 tablespoons brown sugar\\ 
1 tablespoon sugar\\ 
$\frac{1}{4}$ tsp cinnamon\\ 
Dash nutmeg\\ 
1/3 cup raisons\\ 
}

\preparation{
\step For the dough, Scald milk (190 degrees). Soften yeast in lukewarm water (115 degrees).
\step Measure butter, sugar, and salt in mixing bowl. Add milk, stir until butter is melted. When the milk mixture is lukewarm, add yeast.
\step Add half of flour to mixture. Add more flour $\frac{1}{2}$ cup at a time.
\step Turn dough on floured board and allow to rest 10 minutes.
\step Knead the dough until smooth and satiny.\\ 
\step Shape dough and place in oiled bowl. Cover with towel -- let rise out of draft (75 to 85 degrees) 1-1 $\frac{1}{2}$ to 2 hours.
\step Punch down dough -- divide in half\\ 
\step Roll $\frac{1}{2}$ of dough into an oblong 9x8x1/4 inch thick.\\ 
\step Spoon dough with inside ingredients (sugars, cinnamon, nutmeg and raisins).\\ 
\step Roll dough lengthwise, jelly roll fashion. Seal edge firmly. Shape into ring and seal ends together by pinching dough.
\step Cut through ring with scissors to $\frac{1}{2}$ inch from middle in slices 1 inch wide.\\ 
\step Twist each slice slightly on its side. Brush with melted butter and cover. Let the dough rise until it doubles in size.
\step Bake at 375 degrees 25 minutes. Frost while warm with confectionery icing.
}
\end{recipe}
